---
title: "IN2020V08"
author: "Caroline Sutton"
date: "17/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plyr)
library(Rmisc)
library(lattice)
library(tidyr)
library(tidyverse)
library(dplyr)
library(knitr)
library(geosphere)

# read in data
ccomp <- read_csv("data/in2020_v08_samples.csv")
length <- read_csv("data/IN2020_VO8_Lengths.csv")
Shot <- read_csv("data/IN2020_V08_ShotData.csv")
deployments <- read_csv("data/in2020_v08_deployments.csv")

```



```{r catch comp}

# change to uniform names for 'deployment' and 'Accession number' and match species names in length data
ccomp_1 <- ccomp %>% 
  rename(Deployment = 'Operation No', Acc = 'Accession No') %>% 
  select(Voyage, Deployment,Acc,Taxa,CAAB, weight_g =`Weight (g)`, Count,Comments,Storage_temp =`Storage temperature`,Preservative,`Container name`) %>% 
  mutate(Taxa = ifelse(Taxa =="kriffichthys andersoni","Krefftichthys anderssoni",Taxa)) %>%
  mutate(Taxa = ifelse(Taxa =="Aosellota","Asellota",Taxa)) %>%
  mutate(CAAB = ifelse(Taxa =="Krefftichthys anderssoni",37122754,CAAB)) %>% 
  mutate(weight_g = ifelse(weight_g == 0,0.5,weight_g)) %>% 
   mutate(ACat = ifelse(CAAB == 99110232, "Medusa",
                        ifelse(CAAB == 99270010, "Crustacean",
                        ifelse(CAAB == 99901011, "Tunicates",
                        ifelse(CAAB >= 37000000, "Fish",
                        ifelse(CAAB == 36010000, "Chaetognath",
                        ifelse(CAAB >= 35000000, "Tunicates",
                        ifelse(CAAB >= 28800000, "Crustacean",
                        ifelse(CAAB >= 28704000, "Prawn",
                        ifelse(CAAB >= 28700000, "Krill",
                        ifelse(CAAB >= 28399000, "Amphipods",
                        ifelse(CAAB >= 28200000, "Isopods",
                        ifelse(CAAB >= 28081000, "Gnathaphausia",
                        ifelse(CAAB >= 27200000, "Copepod",
                        ifelse(CAAB >= 27100000, "Ostracod",
                        ifelse(CAAB >= 27000000, "Crustacean",
                        ifelse(CAAB >= 24410000, "Gymnosome",
                        ifelse(CAAB >= 24400000, "Pteropod",
                        ifelse(CAAB >= 24000000, "pelagic gastropod",
                        ifelse(CAAB >= 23000000, "Cephalopod",
                        ifelse(CAAB >= 13000000, "worms",
                        ifelse(CAAB >= 13000000, "Other",
                        ifelse(CAAB >= 12000000, "Ctenophore",
                        ifelse(CAAB >= 11123002, "Medusa",
                        ifelse(CAAB >= 11090000, "Siphonophore",
                        ifelse(CAAB >=11000000, "Medusa",
                          "Other")))))))))))))))))))))))))) %>%
  #mutate(ACAT = ifelse(Taxa == "Spongiobranchaea australis", "Other",ACat)) %>% 
  #mutate(ACAT = ifelse(is.na, "Other",ACat)) %>% 
  mutate(ACat = ifelse(Taxa =="Larval Fish", "Fish",
                ifelse(Taxa =="Larval fish", "Fish",
                ifelse(Taxa =="fish", "Fish",   
                ifelse(Taxa =="Fish", "Fish",
                ifelse(Taxa =="Eel Larvae clear", "Fish",
                ifelse(Taxa =="Bathylagus tenuis", "Fish",
                ifelse(Taxa =="Iniea sp.", "Amphipods",
                ifelse(Taxa =="Mixed Prawn larvae", "Prawn",
                ifelse(Taxa ==" Aosellota", "Isopods",
                ifelse(Taxa =="Red Gelatinous", "Siphonophore",
                ifelse(Taxa =="Pelagic worm", "Other",  
                ifelse(Taxa =="Remainder", "Tunicates",  
                ifelse(Taxa =="Spherical eggs", "Other",  
                ifelse(Taxa =="Hyperia medusarium", "Amphipods",     
                ifelse(Taxa =="Aphicaryon acaule", "Siphonophore",      
                ifelse(Taxa =="Salpa thompsoni", "Tunicates",   
                ifelse(Taxa =="Hydromedusa", "Medusa",    
                ifelse(Taxa =="Spongiobranchaea australis", "Gymnosome",
                ifelse(Taxa =="Eusirella spp", "Copepod",   
                ifelse(Taxa =="Asellota", "Isopods",  
                ifelse(Taxa =="Phyllosoma", "Crustacean",  
                ifelse(Taxa =="Senticaudata", "worms",
                ifelse(Taxa =="remainder", "Tunicates",      
                ifelse(Taxa =="eggs", "Other",  
                ifelse(Taxa =="Phronima houses", "Other",
                ifelse(Taxa =="Salpa thompsoni - aggregate", "Tunicates", 
                ifelse(Taxa =="Salpa thompsoni - solitary juv", "Tunicates", 
                ifelse(Taxa =="Salpa thompsoni - solitary", "Tunicates", 
                       ACat))))))))))))))))))))))))))))) %>% 
  separate(Comments, c("sub", "comment"),sep= " ") %>% 
  #filter(sub != "subsample") %>% 
  arrange(-CAAB)

#create higher grouping
ccomp_1 <- ccomp_1 %>% 
  mutate(Taxa_Groups = 
           ifelse(ACat %in% c("Siphonophore","Ctenophore","Medusa"), "Gelatinous_Active",
                  
           ifelse(ACat%in%c("Crustacean","Prawn","Krill","Amphipods","Gnathaphausia", "Isopods",
                            "Gnathapahausia","Copepod","Ostracod"),"Crustaceans",
           ifelse(ACat%in%c("Gymnosome","Pteropod","pelagic gastropod","worms","Other"),"other",
           ACat))))

unique(paste0(ccomp_1$ACat," ",ccomp_1$Taxa_Groups))
check <- select(ccomp_1,ACat,CAAB,Taxa)

species_list <- ccomp_1 %>% 
  distinct(Taxa,.keep_all = TRUE) %>% 
  select(ACat,Taxa,CAAB) %>% 
 # filter(is.na(ACat)) %>% 
  arrange(CAAB)

fixed <-ccomp_1 %>% 
  filter(Preservative !="discarded onboard" & Storage_temp != "-20 degC")
  

Prawns <- ccomp_1 %>% 
  filter(Storage_temp == "-20 degC" & ACat == "Prawn") %>% 
  summarise(weight = sum(weight_g))

Fish <- ccomp_1 %>% 
  filter(Storage_temp != "-20 degC" & ACat == "Fish") %>% 
  summarise(weight = sum(weight_g,na.rm = TRUE))

Inverts <- ccomp_1 %>% 
  filter(Storage_temp != "-20 degC" & ACat != "Fish" & ACat != "Prawns") %>% 
  summarise(weight = sum(weight_g,na.rm = TRUE))

  

                     write.csv(species_list,"Results/SpeciesList.csv")


Prawns <- ccomp_1 %>% 
  filter(ACat =="Prawn" & Storage_temp == "-20 degC" ) %>% 
  select(Deployment,Acc,Taxa)
 

```


RMT 16 net area = 16m^2
speed of vessel on average  = 1kt *** but check with Grafana
time of tow = mins
conversion of kts to kph = kts * 1.852 (kph)
conversion of kph to mpm= kph * 16.667 (mpm)
volume filtered (m^3)= distance (m)* net mouth area (m^2) = ((speed (m/min) * time towed (min)) * net area (m^2))
```{r volume filtered calculation}
Shot_1 <- Shot %>% 
  filter(Category== "Start" | Category == "Stop") %>% 
  filter("Op Number" != '26') %>% 
   select(-Date,-Depth,-'Sea Water Temperature', -Author, - 'Op owner', date = 'Real Date')%>%
  
  #correct entry errors
  # Op  29 start date is incorrect "2020-12-28 15:44:00		 update to 2020-12-26 15:44:00	

  mutate(date = ifelse(date == "2020-12-28 15:44:00","2020-12-26 15:44:00",date)) %>% 
  
   
  #change Latitude to Decimal degrees
  mutate(Lat = Latitude) %>% 
  separate(Lat, c("deg","min","dir"),sep = " ") %>% 
  mutate(deg = as.numeric(deg)) %>% 
  mutate(dir = as.numeric(dir)) %>% 
  mutate(lat_decdeg = -deg + dir/60) %>% 
  #mutate(Date1 = date) %>% 
  #separate(date, c("Date","Time"), sep = " ") %>% 
  mutate(DateR = date) %>% 
  mutate(date = as.POSIXct(date, format = "%d/%m/%Y %H:%M")) %>% 
  
#change longitude to decimal degrees
mutate(Long = Longitude) %>% 
  separate(Long, c("ldeg","lmin","ldir"),sep = " ") %>% 
  mutate(ldeg = as.numeric(ldeg)) %>% 
  mutate(ldir = as.numeric(ldir)) %>% 
  mutate(long_decdeg = -ldeg + ldir/60) %>% 
  select(-deg,-min,-dir,-ldeg,-lmin,-ldir) %>%
  
  #fix up the inconsistencies in site
  separate(Location,c("Site", "S","Cycle","Repeat")) %>% 
  mutate(Site = ifelse(Site =='55',"55S",
                       ifelse(Site == '58', "58S",Site))) %>% 
  arrange(lat_decdeg)
 

# Spitting the data into two tables one for start and one for stop
start <- Shot_1 %>% 
  filter(Category == "Start") 
stop <- Shot_1 %>% 
  filter(Category =="Stop") %>% 
  select('Op number', lat_decdeg,long_decdeg,Site,date,DateR) 


# combining data to have start and stop data for time and position in one row. To calculate distance and time differences
Shot_2 <- start %>%
  left_join(stop, by = 'Op number', suffix= c("_start", "_stop")) %>%
  select(-Category, Site=Site_start, Net_Name = Type, Depth_Stratum = Subject,
         Deployment = 'Op number') %>% 
  separate(Depth_Stratum,c("Depth_Stratum","daylight"),sep = " ") %>% 
  mutate(towtime = difftime(date_stop,date_start, units = "mins")) %>% 
  mutate(Speed_mpm = 1*1.852*16.667) %>% 
  mutate(distance_m = Speed_mpm * towtime) %>%
  mutate(distance_m=as.numeric(distance_m)) %>% 
  mutate(VolumeFiltered_m3 = distance_m * 16) %>% 
  mutate(towtime = difftime(date_stop,date_start, units = "mins")) %>% 
  filter(as.factor(Deployment) != '26')
 
Shot_3 <- Shot_2 %>% 
  select(Site = Site, daylight, Deployment,Depth_Stratum) 
  
  
tally <- Shot_2 %>% 
  #filter(Depth_Stratum == "Epi" | Depth_Stratum =="Lmeso" | Depth_Stratum == "Meso") %>% 
  group_by(Site,daylight, Depth_Stratum) %>% 
  summarise(n=n())
tally_1 <- tally %>% 
  spread(daylight,n)
  
#CR_Date$hours <- with(CR_Date, difftime(pos2,pos1,units="hours") )
#CR_Date
 
Shottest <- Shot_1 %>% 
 mutate(date = ifelse(date == "2020-12-28 15:44:00","2020-12-26 15:44:00",date))
                      

#mutate(Taxa = ifelse(Taxa =="kriffichthys andersoni","Krefftichthys anderssoni",Taxa)) 
```
Length Data
```{R Lengths}
length_1 <- length %>% 
  rename(Acc = 'Acc #') %>% 
  left_join(ccomp_1, by = c("Deployment", "Acc")) %>% 
  left_join(Shot_3, by = "Deployment") %>% 
  select(Voyage= Voyage.x, Site, daylight, Depth_Stratum, Deployment, Acc,Species,Taxa, `Length _mm`)

write.csv(length_1,"Results/IN2020_V08_Lengths.csv")

```

joining shot and catch data
```{r}
deployments_1 <- deployments %>% 
  select(Operation, Tweight_g =`Total Weight (g)`, Sweight_g =`Total Sorted Weight (g)`)



Sol_Micro <-left_join(Shot_2,deployments_1, by= c("Deployment" = "Operation")) %>%  
  mutate(StdW_gm3 = Sweight_g / VolumeFiltered_m3) %>% 
  mutate(Stdw_g1000m3 = StdW_gm3*1000) %>%
  select(-'Message ID', -Latitude,-Longitude, -Site_stop, -date_stop) %>%   filter(Depth_Stratum == "Epi" | Depth_Stratum =="Lmeso" | Depth_Stratum == "Meso")
  
  #group_by(daylight, Depth_Stratum) %>% 
  #summarise(n())

#summary
Sol_Micro_summary <- Sol_Micro %>% 
  group_by(Site,daylight,Depth_Stratum) %>% 
  summarise(n(), mean_g1000m3 = mean(Stdw_g1000m3,na.rm = TRUE), sd = sd(Stdw_g1000m3,na.rm = TRUE)) %>% 
  mutate(mean_g1000m3 = ifelse(daylight == "Night", mean_g1000m3*-1, mean_g1000m3)) %>% 
  mutate(sd = ifelse(daylight == "Night", sd*-1, sd))
  

Sol_Micro_summary$Depth_Stratum <- factor(as.factor(Sol_Micro_summary$Depth_Stratum),levels = c("Lmeso", "Meso", "Epi"))
```


Catch Comp summary
```{r catch summary}
ccomp_2 <- ccomp_1 %>% 
  dplyr::group_by(Deployment,ACat,Taxa_Groups,Taxa) %>% 
  dplyr::summarise(nos= sum(Count, na.rm = TRUE),weight_g = sum(weight_g, na.rm = TRUE))

ccomp_AEC <- ccomp_1 %>% 
  filter(sub !="subsample" | sub !="sub") %>% 
  dplyr::group_by(Taxa_Groups) %>% 
  dplyr::summarise(nos= sum(Count, na.rm = TRUE),weight_kg = round(sum(weight_g, na.rm = TRUE)/1000,digits = 2))
```

Catch comp linked with shot data - ACat
```{r catch comp with shot data - Acoustic Categories}

ccomp_3 <- ccomp_2 %>% 
  left_join(Shot_2, by="Deployment") %>% 
  mutate(Weight_Std_gm3 = weight_g / VolumeFiltered_m3) %>% 
  mutate(Abd_Std_nosm3 = nos / VolumeFiltered_m3) %>% 
  select(Site,daylight,Depth_Stratum,Deployment,ACat,Taxa_Groups,Taxa,
         nos,weight_g,Weight_Std_gm3,Abd_Std_nosm3,
         datetime_UTC_start = date_start,datetime_UTC_stop = date_stop,
         lat_decdeg_start, long_decdeg_start, lat_decdeg_stop, long_decdeg_stop, VolumeFiltered_m3) 

write.csv(ccomp_3,"Results/IN2020_V08_CatchComp.csv")

Species_by_Site <- ccomp_3 %>% 
  group_by(Site) %>% 
  distinct(Taxa, .keep_all = TRUE)
  

#mutate(ACat = ifelse(CAAB == 99110232, "Tunicates",
``` 






Total Standardised catch
```{r total std weight}
TW_std <- ccomp_3 %>% 
  group_by(Site, daylight,Depth_Stratum,Deployment) %>% 
    filter(Depth_Stratum == "Meso"|Depth_Stratum == "Epi"| Depth_Stratum =="Lmeso") %>% 
    mutate(weight_g = ifelse(daylight %in% "Night", weight_g*-1, weight_g)) %>% 
  summarise(TWgm3 = sum(weight_g))



TW_std$Depth_Stratum <- factor(as.factor(TW_std$Depth_Stratum),levels = c("Lmeso", "Meso", "Epi"))
TW_std$Site <- factor(as.factor(TW_std$Site), levels = c("SOTS","55S","58S"))



TW_std_1 <- TW_std %>% 
  group_by(Site,daylight,Depth_Stratum) %>% 
 #mutate(TW_std = TW_std*1000) %>% 
  summarise(n(),TW_std = round(mean(TWgm3,na.rm = TRUE),digits = 2),
            sd = round(sd(TWgm3,na.rm = TRUE),digits = 2)
            )

tw<-ggplot(TW_std_1,
       mapping = aes(x = as.factor(Depth_Stratum), 
                     y = TW_std, fill = daylight))+
  scale_fill_brewer()+
  #geom_errorbar(aes(ymin = sd - 0, ymax= sd + sd)) +
geom_col()+
  coord_flip()+
  facet_grid(~Site)+
  theme_bw()

tw
  
ggsave(tw,filename = "Results/tw.jpg")


# Summary Using SummarySE
TW_summary <- summarySE(TW_std, measurevar = "TWgm3", groupvars = c("Site", "daylight", "Depth_Stratum"))

TWSum_plot <- ggplot(TW_summary,
                     mapping = aes(x = as.factor(Depth_Stratum),
                                   y = TWgm3, fill = daylight))+
  scale_fill_brewer()+
  geom_errorbar(aes(ymin = TWgm3 - sd, ymax= TWgm3 + sd),
                width = 0.4, position = position_dodge(.05)) +
  xlab("Depth Stratum")+
  ylab("Standardised wet weight (g/m^3)")+
 
  #  geom_errorbar(aes(ymin = Length - ci, ymax= Length + ci),
    #            width =.7, position = pd) +
  geom_col()+
  coord_flip()+
  facet_grid(~Site)+
  theme_bw()+
  scale_fill_manual(values=c("light blue","dark blue"))
 
 

TWSum_plot

```


Catch comp grouped for summary graph
NOTE This is not a good example as it averages each value - need to sum first then average for each deployment
```{r summary graph by Acat}
ccomp_4 <-ccomp_3 %>% 
  group_by(Site,daylight,Depth_Stratum,Taxa_Groups, ACat) %>% 
  summarise(n(),
            n =round(mean(nos,na.rm = TRUE),digits = 2), 
            sd_n = round(sd(nos, na.rm=TRUE),digits = 2),
            weight_avg =round(mean(weight_g,na.rm = TRUE),digits = 2),
            sd_w = round(sd(weight_g,na.rm = TRUE),digits = 2)) %>%
  
  filter(Depth_Stratum == "Meso"|Depth_Stratum == "Epi"| Depth_Stratum =="Lmeso") %>% 
  mutate(Wgt= ifelse(daylight %in% "Night", weight_avg*-1, weight_avg)) %>%
  mutate(sd_wgt= ifelse(daylight %in% "Night", sd_w*-1, sd_w)) %>% 
  mutate(numbers = ifelse(daylight %in% "Night", n*-1, n)) %>% 
  mutate(sd_numbers= ifelse(daylight %in% "Night", sd_n*-1, sd_n)) %>% 
  mutate()


 
ccomp_4$Depth_Stratum <- factor(as.factor(ccomp_4$Depth_Stratum),levels = c("Lmeso", "Meso", "Epi"))

ccomp_4$Site <- factor(as.factor(ccomp_4$Site), levels = c("SOTS","55S","58S"))


ggplot(ccomp_4,
       mapping = aes(x =as.factor(Depth_Stratum),
                     y= Wgt))+
  geom_col(aes(fill=Taxa_Groups))+
  coord_flip()+
  facet_grid(~Site)

```
Catch Comp Grouped by ACat - redo the above code to suit

```{r}
```

joining shot and catch data
```{r}
deployments_1 <- deployments %>% 
  select(Operation, Tweight_g =`Total Weight (g)`, Sweight_g =`Total Sorted Weight (g)`)



Sol_Micro <-left_join(Shot_2,deployments_1, by= c("Deployment" = "Operation")) %>%  
  mutate(StdW_gm3 = Sweight_g / VolumeFiltered_m3) %>% 
  mutate(Stdw_g1000m3 = StdW_gm3*1000) %>%
  select(-'Message ID', -Latitude,-Longitude, -Site_stop, -date_stop) %>%   
  filter(Depth_Stratum == "Epi" | Depth_Stratum =="Lmeso" | Depth_Stratum == "Meso") %>% 
  arrange(Deployment)
  
  #group_by(daylight, Depth_Stratum) %>% 
  #summarise(n())

#summary
Sol_Micro_summary <- Sol_Micro %>% 
  group_by(Site,daylight,Depth_Stratum) %>% 
  summarise(n(), mean_g1000m3 = mean(Stdw_g1000m3,na.rm = TRUE), sd = sd(Stdw_g1000m3,na.rm = TRUE)) %>% 
  mutate(mean_g1000m3 = ifelse(daylight == "Night", mean_g1000m3*-1, mean_g1000m3)) %>% 
  mutate(sd = ifelse(daylight == "Night", sd*-1, sd))
  

Sol_Micro_summary$Depth_Stratum <- factor(as.factor(Sol_Micro_summary$Depth_Stratum),levels = c("Lmeso", "Meso", "Epi"))
```

Plotting total catch
```{r}
# all deployments by day, depth
ggplot(Sol_Micro,
       mapping = aes(x = Deployment, 
                     y = Stdw_g1000m3))+
geom_col(aes(fill=daylight) )+
facet_grid(~Depth_Stratum)

Sol_Micro_summary$Depth_Stratum <- factor(as.factor(Sol_Micro_summary$Depth_Stratum),levels = c("Lmeso", "Meso", "Epi"))
Sol_Micro_summary$Site <- factor(as.factor(Sol_Micro_summary$Site), levels = c("SOTS","55S","58S"))

#deployments by depth and day
biomass <-  ggplot(Sol_Micro_summary,
       mapping = aes(x = as.factor(Depth_Stratum), 
                     y = mean_g1000m3, fill = daylight))+
  geom_errorbar(aes(ymin = mean_g1000m3 - 0, ymax= mean_g1000m3 + sd)) +
geom_col()+
  coord_flip()+
  facet_grid(~Site1)+
  theme_bw()
                
  plot(biomass)
ggsave(filename = "Results/biomass.emf")
ggsave(filename = "Results/fbiomass.jpg")

```
Figures
```{r}

Day_Depth <- Sol_Micro %>% 
  #filter(Depth_Stratum == "Epi" | Depth_Stratum =="Lmeso" | Depth_Stratum == "Meso") 
  group_by(daylight,Depth_Stratum) %>% 
  summarise(n(), WSorted_g = mean(Sweight,na.rm = TRUE),sd= sd(Sweight, na.rm = TRUE))
```

                                   
                                  
 

  #calculate distance from position

write.csv(Shot_2,"Results/shotdata.csv")
 
`


    

