---
title: "IN2020V08"
author: "Caroline Sutton"
date: "17/12/2020"
output: html_document
---

#load packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library(tidyverse)
library(dplyr)
library(knitr)

ccomp <- read_csv("data/in2020_v08_samples_validation_210923.csv", col_types = list(Acc_ed = col_character()))
length <- read_csv("data/IN2020_VO8_Lengths.csv")
Shot_withgps <- read_csv("Results/IN2020_V08_Shot_startStop_gps.csv")
deployments <- read_csv("data/in2020_v08_deployments.csv")
ACatDATA <- read_csv("data/MicroDB_Acat_210916.csv")
```


# Standardising Catch Comp Data

```{r Catch comp}
ccomp_1 <-ccomp %>%  
  # remove na values
  drop_na(`Accession No`) %>% 
  mutate(Taxa_updated = ifelse(is.na(Taxa_ed),Taxa,Taxa_ed)) %>% 
  # make a column that includes updateded taxa ID
  mutate(CAAB_updated = ifelse(is.na(CAAB_ed), CAAB,CAAB_ed)) %>% 
  mutate(Taxa_updated = ifelse(is.na(Taxa_ed), Taxa, Taxa_ed))

```

rename columns and taxa
```{r catch comp renaming columns and taxa}

# change to uniform names for 'deployment' and 'Accession number' and match species names in length data
ccomp_2 <- ccomp_1 %>% 
  rename(Deployment = 'Operation No', Acc = 'Accession No', Sample_Type = `Sample Type`) %>% 
  select(Voyage, Deployment,Acc,Acc_ed,Sample_Type,Taxa,CAAB, Taxa_ed,CAAB_ed, weight_g =`Weight (g)`, Count,Comments,Storage_temp =`Storage temperature`,Preservative,`Container name`,Taxa_updated,CAAB_updated) %>% 
  
  # fix up Taxa_updated field field
  mutate(Taxa_updated = ifelse(Taxa_updated == "Larval fish","Larval Fish", Taxa_updated)) %>% 
  mutate(Taxa_updated = ifelse(Taxa_updated == "fish","Fish", Taxa_updated)) %>% 
  mutate(Taxa_updated = ifelse(Taxa_updated == "Melamphaidae-undifferentiated","Melamphaidae - undifferentiated", Taxa_updated)) %>% 
  mutate(Taxa_updated = ifelse(Taxa_updated == "Paralepididae sp. A","Paralepididae - undifferentiated", Taxa_updated)) %>%
  mutate(Taxa_updated = ifelse(Taxa_updated =="Remainder", "remainder", Taxa_updated)) %>% 
  #mutate(Taxa_updated = ifelse(str_detect(Taxa_updated,"Melamphaidae-undifferentiated"), "Melamphaidae - undifferentiated",Taxa_updated)) %>% 
  mutate(Taxa_updated = ifelse(Taxa_updated == "Iniea sp.", "Ihlea spp.", Taxa_updated)) %>% 
  mutate(CAAB_updated = ifelse(Taxa_updated == "Ihlea spp.", 35103904, CAAB_updated)) %>% 
  mutate(Taxa_updated = ifelse(Taxa_updated =="Aosellota","Suborder Asellota - undifferentiated",Taxa_updated)) %>%
  mutate(Taxa_updated = ifelse(Taxa_updated == "Aphicaryon acaule","Amphicaryon acaule",Taxa_updated)) %>% 
  mutate(CAAB_updated = ifelse(Taxa_updated == "Amphicaryon acaule",11095003,CAAB_updated)) %>% 
  mutate(Taxa_updated = ifelse(Taxa_updated == "Krefftichthys andersoni","Krefftichthys anderssoni",Taxa_updated)) %>% 
  mutate(CAAB_updated = ifelse(Taxa_updated == "Krefftichthys anderssoni",37122754,CAAB_updated)) %>% 
  mutate(CAAB_updated = ifelse(Taxa_updated == "Bathylagus spp.",37098903,CAAB_updated)) %>% 
  mutate(CAAB_updated = ifelse(Taxa_updated == "Euphausia spp.", 28702901,CAAB_updated)) %>%
  mutate(CAAB_updated = ifelse(Taxa_updated == "Euchirella spp.", 27212903,CAAB_updated)) %>% 
  mutate(Taxa_updated = ifelse(Taxa_updated == "Scopelogadus beani", "Scopelogadus beanii", Taxa_updated))  %>% 
  mutate(Taxa_updated = str_replace(Taxa_updated,"sp\\.","spp.")) 

# filter(ccomp_2, Taxa_updated == "Krefftichthys anderssoni")
# filter(ccomp_2, CAAB_updated == 37122754)
```

# Adding Acoustic Category ACat
```{r create ACat and higher Taxa_updated grouping}
# correct Taxa_updated data and create ACat field
ccomp_3 <- ccomp_2 %>% 
  mutate(weight_g = ifelse(weight_g == 0,0.5,weight_g)) %>% 
   mutate(ACat = ifelse(CAAB_updated == 99110232, "Medusa",
                        ifelse(CAAB_updated == 99270010, "Crustacean",
                        ifelse(CAAB_updated == 99901011, "Tunicates",
                        ifelse(CAAB_updated >= 37122909, "Fish",
                        ifelse(CAAB_updated >= 37122000, "Fish_GB",
                        ifelse(CAAB_updated >= 37000000, "Fish",
                        ifelse(CAAB_updated == 36010000, "Chaetognath",
                        ifelse(CAAB_updated >= 35000000, "Tunicates",
                        ifelse(CAAB_updated >= 28800000, "Crustacean",
                        ifelse(CAAB_updated >= 28704000, "Prawn",
                        ifelse(CAAB_updated >= 28700000, "Krill",
                        ifelse(CAAB_updated >= 28399000, "Amphipods",
                        ifelse(CAAB_updated >= 28200000, "Isopods",
                        ifelse(CAAB_updated >= 28081000, "Gnathaphausia",
                        ifelse(CAAB_updated >= 27200000, "Copepod",
                        ifelse(CAAB_updated >= 27100000, "Ostracod",
                        ifelse(CAAB_updated >= 27000000, "Crustacean",
                        ifelse(CAAB_updated >= 24410000, "Gymnosome",
                        ifelse(CAAB_updated >= 24400000, "Pteropod",
                        ifelse(CAAB_updated >= 24000000, "pelagic gastropod",
                        ifelse(CAAB_updated >= 23000000, "Cephalopod",
                        ifelse(CAAB_updated >= 13000000, "worms",
                        ifelse(CAAB_updated >= 13000000, "Other",
                        ifelse(CAAB_updated >= 12000000, "Ctenophore",
                        ifelse(CAAB_updated >= 11123002, "Medusa",
                        ifelse(CAAB_updated >= 11100001, "Siph_physonect",  
                        ifelse(CAAB_updated >= 11090000, "Siphonophore",
                        ifelse(CAAB_updated >=11000000, "Medusa",
                          "Other"))))))))))))))))))))))))))))) %>%
  #mutate(ACAT = ifelse(Taxa_updated == "Spongiobranchaea australis", "Other",ACat)) %>% 
  #mutate(ACAT = ifelse(is.na, "Other",ACat)) %>% 
  mutate(ACat = ifelse(Taxa_updated =="Larval Fish", "Fish",
                ifelse(Taxa_updated =="Aosellota", "Other",     
                ifelse(Taxa_updated =="fish", "Fish",
                ifelse(Taxa_updated =="Larval fish", "Fish",
                ifelse(Taxa_updated =="Fish", "Fish",
                ifelse(Taxa_updated =="Eel Larvae clear", "Fish",
                ifelse(Taxa_updated =="Iniea sp.", "Amphipods",
                ifelse(Taxa_updated =="Mixed Prawn larvae", "Prawn",
                ifelse(Taxa_updated =="Suborder Asellota - undifferentiated", "Isopods",
                ifelse(Taxa_updated =="Red Gelatinous", "Siphonophore",
                ifelse(Taxa_updated =="Pelagic worm", "Other",  
                ifelse(Taxa_updated =="Remainder", "Tunicates",  
                ifelse(Taxa_updated =="Spherical eggs", "Other",  
                ifelse(Taxa_updated =="Hyperia medusarium", "Amphipods",     
                ifelse(Taxa_updated =="Aphicaryon acaule", "Siphonophore",      
                ifelse(Taxa_updated =="Salpa thompsoni", "Tunicates",   
                ifelse(Taxa_updated =="Hydromedusa", "Medusa",    
                ifelse(Taxa_updated =="Spongiobranchaea australis", "Gymnosome",
                ifelse(Taxa_updated =="Eusirella spp", "Copepod",   
                ifelse(Taxa_updated =="Asellota", "Isopods",  
                ifelse(Taxa_updated =="Phyllosoma", "Crustacean",  
                ifelse(Taxa_updated =="Suborder Senticaudata - undifferentiated", "worms",
                ifelse(Taxa_updated =="remainder", "Tunicates",      
                ifelse(Taxa_updated =="eggs", "Other",  
                ifelse(Taxa_updated =="Phronima houses", "Other",
                ifelse(Taxa_updated =="Salpa thompsoni - aggregate", "Tunicates", 
                ifelse(Taxa_updated =="Salpa thompsoni - solitary juv", "Tunicates", 
                ifelse(Taxa_updated =="Salpa thompsoni - solitary", "Tunicates", 
                ifelse(Taxa_updated == "Myctophid larvae", "Fish_GB",       
                       ACat)))))))))))))))))))))))))))))) %>% 
  #separate(Comments, c("sub", "comment"),sep= " ") %>% 
  #filter(sub != "subsample") %>% 
  arrange(-CAAB)
#tests
ACat <- ccomp_3 %>% 
  distinct(ACat,Taxa_updated,CAAB_updated)
# filter(ccomp_3, ACat == "Siph_physonect")
```

# Add bladder data information from Micronekton Database
```{r adding bladder data}
### Note this code was used to make the MicroDB_ACat.csv it was then udpated - ie date suffix
# Bladderdata <- MicroDB %>%
#   select(SPCODE, Species_Name,ACat) %>%
#   distinct(Species_Name,.keep_all = TRUE)
# write_csv(Bladderdata,"results/MicroDB_Acat.csv")
#### select appropriate data from MicroDB

### select Fish Bladder data from the ACatDATA
# make necessary edits to ACatDATA
ACatDATA <- ACatDATA %>% 
  mutate(ACat = ifelse(ACat == "FSB", "FGB", ACat))
#test
distinct(ACatDATA,ACat)

## filter for fish data only
ACatDATA_bladder <- ACatDATA %>% 
  filter(ACat == "F" | ACat == "FGB" | ACat =="FnGB")

ccomp_3_ACATDB <- left_join(ccomp_3, ACatDATA_bladder, by = c("Taxa_updated"= "Species_Name")) %>% 
  mutate(ACat = ifelse(is.na(ACat.y),ACat.x,ACat.y)) %>% 
  mutate(ACat = ifelse(ACat == "Fish", "F", ACat)) %>% 
  mutate(ACat = ifelse(ACat == "Fish_GB", "FGB", ACat)) %>% 
  mutate(ACat = ifelse(ACat == "FSB", "FGB", ACat))

distinct(ccomp_3_ACATDB,ACat)
```



#create higher grouping "Taxa_Groups"
```{r creating Taxa_Groups}
ccomp_3_ACATDB_TGroups <- ccomp_3_ACATDB %>% 
  mutate(Taxa_Groups = 
           ifelse(ACat %in% c("Siphonophore","Ctenophore","Medusa"), "Gelatinous_Active",
           ifelse(ACat%in%c("Crustacean","Prawn","Krill","Amphipods","Gnathaphausia", "Isopods",
                            "Gnathapahausia","Copepod","Ostracod"),"Crustaceans",
           ifelse(ACat%in%c("Gymnosome","Pteropod","pelagic gastropod","worms","Other"),"other",
          #ifelse(ACat%in%c("F","FGB"),"F",
           ACat))))
#checking data
# unique(paste0(ccomp_3_ACATDB_TGroups$ACat," ",ccomp_3_ACATDB_TGroups$Taxa_Groups))
# check <- select(ccomp_3_ACATDB_TGroups,ACat,CAAB,Taxa_updated)
# 
# siph <- filter(ccomp_3_ACATDB_TGroups,ACat =="Siphonophore") 
species <- filter(ccomp_3_ACATDB_TGroups,Taxa_updated =="Pyrosoma atlanticum") 
```
<!-- updating data from ANFC - this was done in Ccomp_1 Taxa_updated_Ved, CAAB_Ved -->
<!-- ```{r adding fish Taxa_updated data} -->
<!-- # if Taxa_updated_ed is NA then replace with Taxa_updated otherwise use Taxa_updated_ed -->
<!-- # ccomp_4 <- ccomp_3 %>%  -->
<!-- #   mutate(Taxa_updated = ifelse(is.na(Taxa_updated_ed), Taxa_updated,Taxa_updated_ed)) %>%  -->
<!-- #   mutate(CAAB_updated = ifelse(is.na(CAAB_ed), CAAB,CAAB_ed)) -->
<!-- ``` -->

#create highest grouping "Acoustic_Category"
```{r creating Acoustic_Category}
ccomp_3_ACATDB_Acoustic_Category <- ccomp_3_ACATDB_TGroups %>% 
  mutate(Acoustic_Category = 
           ifelse(ACat %in% c("Siphonophore","Ctenophore","Medusa","Chaetognath","Tunicates"), "G_nGB",
           ifelse(ACat %in% c("Siph_physonect"), "G_GB",
                  
           ifelse(ACat%in%c("Crustacean","Prawn","Krill","Amphipods","Gnathaphausia", "Isopods",
                            "Gnathapahausia","Copepod","Ostracod"),"Crustaceans",
           ifelse(ACat%in%c("Gymnosome","Pteropod","pelagic gastropod","worms","Other"),"other",
          #ifelse(ACat%in%c("F","FGB"),"F",
           ACat)))))


#checking data
# print Acoustic_Category and ACat
unique(paste0(ccomp_3_ACATDB_Acoustic_Category$Acoustic_Category," ",ccomp_3_ACATDB_Acoustic_Category$ACat))

check <- select(ccomp_3_ACATDB_Acoustic_Category,Acoustic_Category,CAAB,Taxa_updated)

siph <- filter(ccomp_3_ACATDB_Acoustic_Category,ACat =="Siphonophore") %>% 
  distinct(Taxa_updated)

# Table of Taxa Groupings
Taxa_Groupings <- ccomp_3_ACATDB_Acoustic_Category %>% 
select(Acoustic_Category,Taxa_Groups,ACat) %>% 
  arrange(Acoustic_Category) %>% 
    distinct(Acoustic_Category,ACat,Taxa_Groups)
  
  
```



#filter data to exclude Subsamples, data where the Acc has been split, and Gut samples
```{r filter Samples}
#list sample types
#unique(ccomp_4$Sample_Type)
# choose only "S" which is a full sample (not subsampele, renamedsplit or gut sample)
ccomp_4 <- ccomp_3_ACATDB_Acoustic_Category %>%
  filter(Sample_Type == "S") %>% 
  select(Voyage,Deployment,Acc,Acc_ed,ACat,Taxa_Groups,Acoustic_Category, CAAB,Taxa_updated,CAAB_updated,Taxa_updated,Count,weight_g,Storage_temp,Preservative) 



```


```{r data outputs}
species_list <- ccomp_4 %>% 
  distinct(Taxa_updated,.keep_all = TRUE) %>% 
  select(ACat,Taxa_updated,CAAB_updated) %>% 
 # filter(is.na(ACat)) %>% 
  arrange(CAAB_updated)
write.csv(species_list,"Results/SpeciesList.csv")

# Sample subsets by fixative and Taxa_updated group
fixed <-ccomp_3_ACATDB_TGroups %>% 
  filter(Preservative !="discarded onboard" & Storage_temp != "-20 degC")
  
Prawns <- ccomp_3_ACATDB_TGroups %>% 
  filter(Storage_temp == "-20 degC" & ACat == "Prawn") %>% 
  summarise(weight = sum(weight_g))

Fish <- ccomp_3_ACATDB_TGroups %>% 
  filter(Storage_temp != "-20 degC" & ACat == "Fish") %>% 
  summarise(weight = sum(weight_g,na.rm = TRUE))

Inverts <- ccomp_3_ACATDB_TGroups %>% 
  filter(Storage_temp != "-20 degC" & ACat != "Fish" & ACat != "Prawns") %>% 
  summarise(weight = sum(weight_g,na.rm = TRUE))

Prawns <- ccomp_3_ACATDB_TGroups %>% 
  filter(ACat =="Prawn" & Storage_temp == "-20 degC" ) %>% 
  select(Deployment,Acc,Taxa_updated)
```

# Shot Data

## Volume Filtered Calculation
RMT 16 net area = 16m^2
speed of vessel on average  = 1kt *** but check with Grafana
time of tow = mins
conversion of kts to kph = kts * 1.852 (kph)
conversion of kph to mpm= kph * 16.667 (mpm)
volume filtered (m^3)= distance (m)* net mouth area (m^2) = ((speed (m/min) * time towed (min)) * net area (m^2))

```{r volume filtered calculation}
# don't need this code b/c shot data has it own file now. Need to use the shot data with added gps distance calculation and gps VFiltered calculation. 
# Shot_1 <- Shot %>% 
#   filter(Category== "Start" | Category == "Stop") %>% 
#   filter("Op Number" != '26') %>% 
#    select(-Date,-Depth,-'Sea Water Temperature', -Author, - 'Op owner', date = 'Real Date')%>%
#   
#   #correct entry errors
#   # Op  29 start date is incorrect "2020-12-28 15:44:00		 update to 2020-12-26 15:44:00	
#   mutate(date = ifelse(date == "2020-12-28 15:44:00","2020-12-26 15:44:00",date)) %>% 
#   
#    
#   #change Latitude to Decimal degrees
#   mutate(Lat = Latitude) %>% 
#   separate(Lat, c("deg","min","dir"),sep = " ") %>% 
#   mutate(deg = as.numeric(deg)) %>% 
#   mutate(dir = as.numeric(dir)) %>% 
#   mutate(lat_decdeg = -deg + dir/60) %>% 
#   #mutate(Date1 = date) %>% 
#   #separate(date, c("Date","Time"), sep = " ") %>% 
#   mutate(DateR = date) %>% 
#   mutate(date = as.POSIXct(date, format = "%d/%m/%Y %H:%M")) %>% 
#   
# #change longitude to decimal degrees
# mutate(Long = Longitude) %>% 
#   separate(Long, c("ldeg","lmin","ldir"),sep = " ") %>% 
#   mutate(ldeg = as.numeric(ldeg)) %>% 
#   mutate(ldir = as.numeric(ldir)) %>% 
#   mutate(long_decdeg = -ldeg + ldir/60) %>% 
#   select(-deg,-min,-dir,-ldeg,-lmin,-ldir) %>%
#   
#   #fix up the inconsistencies in site
#   separate(Location,c("Site", "S","Cycle","Repeat")) %>% 
#   mutate(Site = ifelse(Site =='55',"55S",
#                        ifelse(Site == '58', "58S",Site))) %>% 
#   arrange(lat_decdeg)
#  
# # Spitting the data into two tables one for start and one for stop
# start <- Shot_1 %>% 
#   filter(Category == "Start") 
# stop <- Shot_1 %>% 
#   filter(Category =="Stop") %>% 
#   select('Op number', lat_decdeg,long_decdeg,Site,date,DateR) 
# ##Volume Filtered by calculating distance traveled by Ships Speed and tow time
# # combining data to have start and stop data for time and position in one row. To calculate distance and time differences
# Shot_2 <- start %>%
#   left_join(stop, by = 'Op number', suffix= c("_start", "_stop")) %>%
#   select(-Category, Site=Site_start, Net_Name = Type, Depth_Stratum = Subject,
#          Deployment = 'Op number') %>% 
#   separate(Depth_Stratum,c("Depth_Stratum","daylight"),sep = " ") %>% 
#   mutate(towtime = difftime(date_stop,date_start, units = "mins")) %>% 
#   mutate(Speed_mpm = 1*1.852*16.667) %>% 
#   mutate(distance_m_byspeed = Speed_mpm * towtime) %>%
#   mutate(distance_m_byspeed=as.numeric(distance_m_byspeed)) %>% 
#   mutate(VolumeFiltered_m3_speed = distance_m_byspeed * 16) %>% 
#   mutate(towtime = difftime(date_stop,date_start, units = "mins")) %>% 
#   filter(as.factor(Deployment) != '26') %>% 
#   select(-"S", -"Cycle",-"Repeat") %>% 
#   arrange()
# write.csv(Shot_2,"Results/IN2020_V08_Shot_startStop.csv")
#  
# Shot_3 <- Shot_2 %>% 
#   select(Site = Site, daylight, Deployment,Depth_Stratum) 
#   
#   
# tally <- Shot_2 %>% 
#   #filter(Depth_Stratum == "Epi" | Depth_Stratum =="Lmeso" | Depth_Stratum == "Meso") %>% 
#   group_by(Site,daylight, Depth_Stratum) %>% 
#   summarise(n=n())
# tally_1 <- tally %>% 
#   spread(daylight,n)
#   
# #CR_Date$hours <- with(CR_Date, difftime(pos2,pos1,units="hours") )
# #CR_Date
#  
# Shottest <- Shot_1 %>% 
#  mutate(date = ifelse(date == "2020-12-28 15:44:00","2020-12-26 15:44:00",date))
#                       
# #mutate(Taxa_updated = ifelse(Taxa_updated =="kriffichthys andersoni","Krefftichthys anderssoni",Taxa_updated)) 
```
# exploring shot data
```{r shot data exploration}



ggplot(data = (filter(Shot_withgps,Depth_Stratum == "Lmeso" |Depth_Stratum=="Meso" | Depth_Stratum == "Epi")), 
               aes(VolumeFiltered_m3_speed,Deployment, colour = Depth_Stratum)) +
 
  geom_point()+
facet_grid(~Site)

ggplot(filter(Shot_withgps,Depth_Stratum == "Lmeso" |Depth_Stratum=="Meso" | Depth_Stratum == "Epi"), aes(x=Deployment,colour = Depth_Stratum)) + 
  geom_point(aes(y=VolumeFiltered_m3_speed, shape="V_speed")) + 
  geom_point(aes(y=VolumeFiltered_m3_gps, shape="V_gps")) 
```


# Length Data
```{r Lengths}

# selecting data from ccomp_4 and length  to make the join more manageable
ccomp_4_forlengthjoin <- select(ccomp_4, Deployment, Acc, Acc_ed,Taxa_updated, CAAB_updated)

length_1 <- length %>% 
  rowid_to_column("ID") %>% 
  rename(Acc = 'Acc #') %>% 
  select(-Voyage,-Net_Name)

# joining length data to the catch comp and site data for graphing
length_2<- length_1 %>% 
  left_join(ccomp_4_forlengthjoin, by = c("Deployment", "Acc")) %>% 
  distinct(ID, .keep_all = TRUE) %>% 
  left_join(Shot_withgps, by = "Deployment") %>% 
  distinct(ID, .keep_all = TRUE) %>% 
  arrange()

# calculate average lengths
length_2_avg <- length_2 %>% 
  rename(length_mm = `Length _mm`) %>% 
  group_by(Deployment,Acc_ed) %>% 
  summarise(n(),AvgL_mm = mean(length_mm))
  
Dups <-length_2[duplicated(length_2$ID), ]

#plot length data
  length_2_sites <-  select(length_2, Site, daylight, Depth_Stratum, Deployment, Acc, Acc_ed, Species,Taxa_updated, `Length _mm`) %>% 
   filter(Depth_Stratum == "Meso"|Depth_Stratum == "Epi"| Depth_Stratum =="Lmeso") %>%     
  filter(`Length _mm`< 5500)
  

  
write.csv(length_2_sites,"Results/IN2020_V08_Lengths.csv")

# ggplot(length_2_sites, aes(y = Depth_Stratum, x = `Length _mm`)) +
#   geom_point()
```

## add in the average length data to the catch comp
```{r adding in length data}
  
ccomp_5 <- left_join(ccomp_4, length_2_avg, by = c("Deployment", "Acc_ed")) 

#dupes <- get_dupes(ccomp_2_ACATDB_length
 
# filter(ccomp_5,Deployment == 39, Acc_ed== 19)
```


# Shot Data and Catch Data

## Joining Shot and Catch data for total weight estimates
```{r join catch comp and shot data}
deployments_1 <- deployments %>% 
  select(Operation, Tweight_g =`Total Weight (g)`, Sweight_g =`Total Sorted Weight (g)`)
  Sol_Micro <-left_join(Shot_withgps,deployments_1, by= c("Deployment" = "Operation")) %>%  
  #use updated shot data to provide the option of standardising catch by VF as estiamted by gps
  #Sol_Micro <-left_join(Shot_2,deployments_1, by= c("Deployment" = "Operation")) %>% 
  mutate(StdW_gm3_gps = Sweight_g / VolumeFiltered_m3_gps) %>% 
  mutate(StdW_gm3_sp = Sweight_g / VolumeFiltered_m3_speed) %>% 
    
    #### change the estimate by gps and speed here #######
  #mutate(Stdw_g1000m3 = StdW_gm3_sp*1000) %>%
  mutate(Stdw_g1000m3 = StdW_gm3_gps*1000) %>%
    ##############################################################
    
  select(-'Message ID', -Latitude,-Longitude, -Site_stop, -date_stop) %>%   filter(Depth_Stratum == "Epi" | Depth_Stratum =="Lmeso" | Depth_Stratum == "Meso")
  
  #group_by(daylight, Depth_Stratum) %>% 
  #summarise(n())
#summary
Sol_Micro_summary <- Sol_Micro %>% 
  group_by(Site,daylight,Depth_Stratum) %>% 
  summarise(n(), mean_g1000m3 = mean(Stdw_g1000m3,na.rm = TRUE), sd = sd(Stdw_g1000m3,na.rm = TRUE)) %>% 
  mutate(mean_g1000m3 = ifelse(daylight == "Night", mean_g1000m3*-1, mean_g1000m3)) %>% 
  mutate(sd = ifelse(daylight == "Night", sd*-1, sd))
  
Sol_Micro_summary$Depth_Stratum <- factor(as.factor(Sol_Micro_summary$Depth_Stratum),levels = c("Lmeso", "Meso", "Epi"))
```
# summarising data by species to remove duplications of species per shot
```{r catch comp summary}
#summarise data by species for each Deployment 
## note that this will now remove the Acc
## for example Larval Fish often had two accession numbers - one for F and one for Eth preserved samples
ccomp_5_summary<- ccomp_5 %>% 
  group_by(Deployment,ACat,Taxa_Groups,Acoustic_Category,Taxa_updated,CAAB_updated) %>% 
  summarise(nos= sum(Count, na.rm = TRUE),weight_g = sum(weight_g, na.rm = TRUE), AvgL_mm) %>% 
  rowid_to_column("ID")
#ccomp_AEC <- ccomp_1 %>% 
#  filter(sub !="subsample" | sub !="sub") %>% 
#  dplyr::group_by(Taxa_updated) %>% 
 # dplyr::summarise(nos= sum(Count, na.rm = TRUE),weight_kg = round(sum(weight_g, na.rm = TRUE)/1000,digits = 2))

# filter(ccomp_4,Deployment == 39, Acc== 19)
```

# Bringing in Shot Data with Volume Filtered as estimated by the Ship's position

## Standardising the catch comp with Volumen Filtered
```{r Standardising catch data }
ccomp_6_SumShot <- ccomp_5_summary %>% 
  left_join(Shot_withgps, by="Deployment") %>% 
  mutate(Weight_Std_gm3_sp = weight_g / VolumeFiltered_m3_speed) %>%
  mutate(Weight_Std_gm3_gps = weight_g / VolumeFiltered_m3_gps) %>%
  mutate(Abd_Std_nosm3_sp = nos / VolumeFiltered_m3_speed) %>% 
  mutate(Abd_Std_nosm3_gps = nos / VolumeFiltered_m3_gps) %>% 
  select(ID,Site,daylight,Depth_Stratum,Deployment,
         ACat,Taxa_Groups,Acoustic_Category, Taxa_updated,CAAB_updated,
         nos,weight_g,
         Weight_Std_gm3_gps, Abd_Std_nosm3_gps, #select gps 
         Weight_Std_gm3_sp, Abd_Std_nosm3_sp, #select  speed
         AvgL_mm,
         datetime_UTC_start = date_start,datetime_UTC_stop = date_stop,
         lat_decdeg_start, long_decdeg_start, lat_decdeg_stop, long_decdeg_stop, VolumeFiltered_m3_speed,VolumeFiltered_m3_gps) %>% 
  #making sure dupicate row are ignored
  distinct(ID,.keep_all = TRUE)


  
tally <- Shot_withgps %>% 
  mutate(Depth_Stratum = ifelse(Depth_Stratum == "Epi" | 
                                  Depth_Stratum =="Lmeso" | 
                                  Depth_Stratum == "Meso"|
                                  Depth_Stratum == "Integrated",Depth_Stratum,"Targetted" )) %>% 
  group_by(Site,daylight, Depth_Stratum) %>% 
  summarise(n=n()) %>% 
#tally_1 <- tally %>% 
  spread(daylight,n)
```
worms
# Create Taxa_PLAOS"
```{r Taxa_PLAOS}

ccomp_6_SumShot_PLAOS <- ccomp_6_SumShot %>%
  mutate(Taxa_PLAOS = 
           ifelse(ACat %in% c("Amphipods","Copepod","Ostracod","Isopods","Gnathaphausia"), "Crustacean",
           ifelse(ACat %in% c("worms","pelagic gastropod","Pteropod","Gymnosome"), "Other",
           ACat))) %>% 
  mutate(Taxa_PLAOS = ifelse(ACat == "Tunicates", "Salp",Taxa_PLAOS)) %>% 
  mutate(Taxa_PLAOS = ifelse(Taxa_updated == "Pyrosoma atlanticum", "Pyrosome",Taxa_PLAOS))
  
  ccomp_6_SumShot_PLAOS <- ccomp_6_SumShot_PLAOS %>% 
  ungroup()


taxagroups <- ccomp_6_SumShot_PLAOS %>% 
  select(Acoustic_Category,Taxa_PLAOS) %>% 
  distinct(Acoustic_Category,Taxa_PLAOS)


#filter out small <20 mm but don't exlude the physonects
ccomp_6_SumShot_PLAOS_20mm_design <- ccomp_6_SumShot_PLAOS %>% 
  filter(ACat == "Siph_physonect" |  AvgL_mm >= 20) %>% 
   filter(Depth_Stratum == "Meso"|Depth_Stratum == "Epi"| Depth_Stratum =="Lmeso")

```

# catch comp
```{r write catch comp}
write.csv(ccomp_6_SumShot_PLAOS_20mm_design,"Results/IN2020_V08_CatchComp.csv")
write.csv(ccomp_6_SumShot_PLAOS, "Results/IN2020_V08_CatchComp_allsites.csv")
```

# Filtered for Micronekton 
```{r filtering for Micronekton - removing small biota}
# Micronekton only !!!
ccomp_6_SumShot_Micro <- ccomp_6_SumShot %>% 
  filter(AvgL_mm >=20) 
  #filter(ACat != "Tunicates" & ACat != "Medusa") 
write.csv(ccomp_6_SumShot_Micro,"Results/IN2020_V08_CatchComp_Micro20mm.csv")

ccomp_6_SumShot_Micro <- ccomp_6_SumShot %>% 
  filter(AvgL_mm >=15) 
  #filter(ACat != "Tunicates" & ACat != "Medusa") 
write.csv(ccomp_6_SumShot_Micro,"Results/IN2020_V08_CatchComp_Micro15mm.csv")
``` 
