---
title: "Summary data"
author: "sutton"
date: "24/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# library(plyr)
# library(Rmisc)
# library(lattice)
# library(tidyr)
library(tidyverse)
# library(gridExtra)
library(dplyr)
library(knitr)
library(ggpubr) # nice plots
library(rstatix) # pip freindly stats
# library(geosphere)
# library(janitor)

# data filtered for <20cm, includes physonects, design deployments only
SOLACE <- read_csv("Results/IN2020_V08_CatchComp.csv")

```


```{r cummulative biomass}
distinct(SOLACE,Depth_Stratum)

SOLACE$Depth_Stratum <- factor(as.factor(SOLACE$Depth_Stratum),levels = c("Lmeso", "Meso", "Epi"))
SOLACE$Site <- factor(as.factor(SOLACE$Site), levels = c("SOTS","55S","58S"))

SOLACE_cumsum <- SOLACE %>% 
  select(Site,Acoustic_Category,Taxa_updated,weight_g) %>% 
  group_by(Site,Taxa_updated) %>% 
  summarise(weight = sum(weight_g)) %>% 
 # ungroup() %>% 
  arrange(Site,-weight) %>% 
  mutate(cumsum = cumsum(weight)) %>% 
  mutate(percent =round(weight/sum(weight),2)) %>%
  mutate(cumpercent = round(cumsum/sum(weight),2))  
```


```{r sum biomass by deployment}

### Total Biomass #############################

# sum biomass for each deployment
Biomass_deployment <- SOLACE %>% 
  select(Site, daylight,Depth_Stratum, Deployment, Taxa_updated,Acoustic_Category, Abd_Std_nosm3_sp,Weight_Std_gm3_sp) %>%
  dplyr::group_by(Site, daylight, Depth_Stratum,Deployment) %>% 
  dplyr::summarise(StdWt = sum(Weight_Std_gm3_sp), 
                   StdAbd = sum(Abd_Std_nosm3_sp)) %>% 
  dplyr::ungroup() %>% 
  mutate(logwt = log(StdWt))

# average biomass for each treatment by Site/daylight/Depth_Stratum
Biomass_Design <- Biomass_deployment %>% 
  group_by(Site,daylight,Depth_Stratum) %>% 
  summarise(StdWt_avg = mean(StdWt),sd = sd(StdWt)) %>% 
  ungroup()

#### Acoustic_Category ####################
# sum biomass for each Acoustic_Category within each deployment
Biomass_AC <- SOLACE %>% 
  select(Site, daylight,Depth_Stratum, Deployment, Taxa_updated,Acoustic_Category, Abd_Std_nosm3_sp,Weight_Std_gm3_sp) %>%
  dplyr::group_by(Site, daylight, Depth_Stratum,Deployment,Acoustic_Category) %>% 
  dplyr::summarise(StdWt = sum(Weight_Std_gm3_sp), 
                   StdAbd = sum(Abd_Std_nosm3_sp)) %>% 
  mutate(StdWt = ifelse(daylight %in% "Night", StdWt*-1, StdWt)) %>% 
  dplyr::ungroup() 
# Average biomass for each Acoustic_Category  by Site/daylight/Depth_Stratum
Biomass_Design_AvgAC <- Biomass_AC %>% 
  group_by(Site,daylight,Depth_Stratum,Acoustic_Category) %>% 
  summarise(StdWt_AC = mean(StdWt))


```
# Plots 
## Total Average Biomass

Sutton Code
```{r total weight}

Biomass_Desgin_daynight <- Biomass_Design %>% 
   mutate(StdWt = ifelse(daylight %in% "Night", StdWt_avg*-1, StdWt_avg)) %>% 
  mutate(sd = ifelse(daylight %in% "Night", sd*-1, sd)) 


tw<-ggplot(Biomass_Desgin_daynight,
       mapping = aes(x = as.factor(Depth_Stratum),
                     y = StdWt, fill = daylight))+
  geom_rect(ymax= -Inf, ymin= 0, xmin=-Inf, xmax=Inf, fill= "grey", alpha= 0.2) +
      scale_fill_manual(values = c("light blue","dark blue")) +
  #scale_fill_brewer()+
  geom_errorbar(aes(ymin = StdWt - sd, ymax= StdWt + sd),
                width = 0.4, position = position_dodge(0)) +
geom_col()+
  geom_hline(yintercept=0)+
  coord_flip()+
  facet_grid(Site ~ .,switch = "x")+
  #theme_bw()
 labs(y="Total Average Biomass (g/m^3)", x="Depth Stratum") 
  

tw

```

Sutton code with ACat
```{r sutton code with Acat}
# suttons way
ggplot(Biomass_Design_AvgAC,
       mapping = aes(x = Depth_Stratum ,y=StdWt_AC, fill = Acoustic_Category))+
     #scale_fill_manual(values = c("purple","orange", "blue","dark blue","light blue","light pink","light green")) +
  geom_rect(ymax= -Inf, ymin= 0, xmin=-Inf, xmax=Inf, fill= "grey", alpha= 0.2) +
  geom_col()+
  #geom_hline(yintercept=0)+
  coord_flip()+
  facet_grid(Site ~.,switch = "x")+  
  labs(x="Depth Stratum", y="Avgerage Biomass g/m^3)") 
   

ggplot(Biomass_Design_AvgAC,
       mapping = aes(x = Depth_Stratum ,y=StdWt_AC, fill = Acoustic_Category))+
     scale_fill_manual(values = c("purple","orange", "blue","dark blue","light blue", "light pink","light green")) +
  geom_rect(ymax= -Inf, ymin= 0, xmin=-Inf, xmax=Inf, fill= "grey", alpha= 0.2) +
  geom_col()+
  #geom_hline(yintercept=0)+
  coord_flip()+
  facet_grid(Site ~.,switch = "y")+  
  labs(x="Depth Stratum", y="Avgerage Biomass g/m^3)") 
   

# annabelles way
Biomass_Design_AvgAC <- Biomass_Design_AvgAC %>% 
   mutate(StdWt_AC = ifelse(daylight %in% "Night", StdWt_AC*-1, StdWt_AC)) 


day_values <- Biomass_Design_AvgAC%>% 
  filter(daylight== "Day")
night_values <- Biomass_Design_AvgAC %>% 
  filter(daylight== "Night")
night_values <- night_values %>%
  mutate_if(is.numeric, funs(. * -1))

ggplot(Biomass_Design_AvgAC, aes(x= StdWt_AC, y= Depth_Stratum, fill= Acoustic_Category))+
geom_rect(xmax= -Inf, xmin= 0, ymin=-Inf, ymax=Inf, fill= "lightgray", alpha= 0.2) +
  geom_bar(data= day_values, stat= "identity") + 
  geom_bar(data= night_values, stat= "identity") + 
    facet_grid(rows= vars(Site), scales = "fixed") + 
    #scale_fill_manual(values = c("#7F3C8D","#3969AC", "#11A579","#7F3C8D","#3969AC", "#11A579","#7F3C8D","#3969AC", "#11A579")) +
  geom_vline(xintercept= 0) +
  labs(y="Depth Stratum", x="Avgerage Biomass g/m^3)") 
  
  

```


## Taxa_PLAOS 
```{r Taxa_PLAOS}

# sum biomass for each Taxa_PLAOS within each deployment
Biomass_Taxa_PLAOS <- SOLACE %>% 
  select(Site, daylight,Depth_Stratum, Deployment, Taxa_updated, Acoustic_Category,Taxa_PLAOS, Abd_Std_nosm3_sp,Weight_Std_gm3_sp) %>%
  dplyr::group_by(Site, daylight, Depth_Stratum,Deployment,Acoustic_Category,Taxa_PLAOS) %>% 
  dplyr::summarise(StdWt = sum(Weight_Std_gm3_sp), 
                   StdAbd = sum(Abd_Std_nosm3_sp)) %>% 
  mutate(StdWt = ifelse(daylight %in% "Night", StdWt*-1, StdWt)) %>% 
  dplyr::ungroup() 

# Average biomass for each Taxa_PLAOS  by Site/daylight/Depth_Stratum
Biomass_Design_AvgTP <- Biomass_Taxa_PLAOS %>% 
  group_by(Site,daylight,Depth_Stratum,Acoustic_Category,Taxa_PLAOS) %>% 
  summarise(StdWt_TP = mean(StdWt))


##PLOT

ggplot(Biomass_Design_AvgTP,
       mapping = aes(x = Depth_Stratum ,y=StdWt_TP, fill = Taxa_PLAOS))+
     #scale_fill_manual(values = c("purple","orange", "blue","dark blue","light blue","light pink","light green")) +
  geom_rect(ymax= -Inf, ymin= 0, xmin=-Inf, xmax=Inf, fill= "grey", alpha= 0.2) +
  geom_col()+
  #geom_hline(yintercept=0)+
  coord_flip()+
  facet_grid(rows= vars(Site), cols= vars(Acoustic_Category), scales = "free") + 
  labs(x="Depth Stratum", y="Avgerage Biomass g/m^3)") 


```

Annabelle's code
```{r AE code}
Biomass_Desgin_AE <- Biomass_Design

# Biomass_Desgin_AE$Depth_Stratum <- factor(as.factor(Biomass_Desgin_AE$Depth_Stratum), levels=c("Lmeso","Meso","Epi"))
# Biomass_Desgin_AE$Site <- factor(as.factor(Biomass_Desgin_AE$Site), levels= c("SOTS", "55S", "58S"))

day_values <- Biomass_Desgin_AE%>% 
  filter(daylight== "Day")

night_values <- Biomass_Desgin_AE %>% 
  filter(daylight== "Night")
night_values <- night_values %>%
  mutate_if(is.numeric, funs(. * -1))


ggplot(Biomass_Desgin_AE, aes(x= StdWt_avg, y= Depth_Stratum, fill= Depth_Stratum))+
  geom_rect(xmax= -Inf, xmin= 0, ymin=-Inf, ymax=Inf, fill= "lightgray", alpha= 0.2) +
  geom_bar(data= day_values, stat= "identity") + 
  geom_bar(data= night_values, stat= "identity") + 
    facet_grid(rows= vars(Site), scales = "fixed") + 
    scale_fill_manual(values = c("#7F3C8D","#3969AC", "#11A579","#7F3C8D","#3969AC", "#11A579","#7F3C8D","#3969AC", "#11A579")) +
  geom_vline(xintercept= 0) + 
  labs(y="Depth Stratum", x="log (Biomass g/m3)") 
```




```{r summary stats}
Biomass_deployment$Depth_Stratum <- factor(as.factor(Biomass_deployment$Depth_Stratum), levels=c("Lmeso","Meso","Epi"))
Biomass_deployment$Site <- factor(as.factor(Biomass_deployment$Site), levels=c("SOTS","55S","58S"))
Biomass_deployment$daylight <- factor(as.factor(Biomass_deployment$daylight), levels=c("Day","Night"))

Biomass_design <-Biomass_deployment %>% 
  mutate(logwt = log(Weight)) %>% 
  group_by(Site, daylight, Depth_Stratum) %>% 
  get_summary_stats(Weight, type = "mean_sd")
```
boxplot
```{r boxplot}
bxp <- ggboxplot(
  Biomass_deployment, x = "daylight", y = "logwt", 
  color = "Depth_Stratum", palette = "jco", facet.by = "Site"
  )
bxp
```

barplot weight
```{r barplot weight}
Biomass_design_daylight <- Biomass_design %>% 
  mutate(mean = ifelse(daylight %in% "Night", mean*-1, mean)) 


barp <-ggplot(Biomass_design_daylight,
       mapping = aes(x = as.factor(Depth_Stratum),
                     y = mean, fill = daylight))+
  scale_fill_brewer()+
  geom_errorbar(aes(ymin = mean - sd, ymax= mean + sd),
                width = 0.4, position = position_dodge(0)) +
geom_col()+
  coord_flip()+
  facet_grid(~Site)+
  theme_bw()
barp

```


barplot logwt
```{r barplot weight}
barp <-ggplot(Biomass_design,
       mapping = aes(x = as.factor(Depth_Stratum),
                     y = mean, fill = daylight))+
  scale_fill_brewer()+
  geom_errorbar(aes(ymin = mean - sd, ymax= mean + sd),
                width = 0.4, position = position_dodge(0)) +
geom_col()+
  coord_flip()+
  facet_grid(~Site)+
  theme_bw()
barp

```

outliers
```{r outliers}
Biomass_deployment %>%
  group_by(Site,Depth_Stratum) %>%
  identify_outliers(logwt)
# dont get this
# deployments 8 and 13 are outliers but not extreme. Outliers are not obvious when using Site alone, all 3 factors or Site&daylight
```


normality

In the QQ plot, as all the points fall approximately along the reference line, we can assume normality. 

This conclusion is supported by the Shapiro-Wilk test, if the p-value is not significant. 
then  can assume normality.
```{r normality}
model  <- lm(logwt ~ Site*daylight*Depth_Stratum, data = Biomass_deployment)
# Create a QQ plot of residuals
ggqqplot(residuals(model))
# Compute Shapiro-Wilk test of normality
shapiro_test(residuals(model))

# probs not quite normally distributed - should transform

```
normality by groups
```{r shapiro test by groups}
Biomass_deployment %>%
  group_by(Site, daylight, Depth_Stratum) %>%
  shapiro_test(Weight)
```



QQ test
```{r qqtest}
ggqqplot(BulkBiomass, "Weight", ggtheme = theme_bw()) +
  facet_grid(Site + daylight ~ Depth_Stratum, labeller = "label_both")
```

homgeneity
```{r levenes}
BulkBiomass %>% levene_test(Weight ~ Site*daylight*Depth_Stratum)
# not significant assume homogeneity
```

Anova
```{r anova}
bio.aov <-  BulkBiomass%>% anova_test(Weight ~ Depth_Stratum*daylight*Site)
bio.aov
# there was a 3way interaction F(2,22)= 3.04, p = 0.039
```
Post hoc tests
2 way interactions
decide which two variables will form the simple two-way interactions and which variable will act as the third (moderator) variable. 

```{r post hoc 2 way interaction}
# Group the data by gender and 
# fit simple two-way interaction 
model  <- lm(Weight ~ daylight*Site*Depth_Stratum, data = Biomass_deployment)
Biomass_deployment %>%
  group_by(daylight) %>%
  anova_test(Weight ~ Depth_Stratum*Site, error = model)
```