---
title: "SOLACE_RMT_analysis"
author: "Caroline Sutton"
date: "28/10/2021"
output:
 html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo=TRUE,
  warning = FALSE,
  message = FALSE,
  results = 'asis',
  fig.align = 'center')

#Load libraries
library(tidyverse)
library(knitr)
library(kableExtra)
library(dplyr)
library(ggplot2)
library(tidyr)
SOLACE <- read_csv("Results/IN2020_V08_CatchComp.csv")

```


### Data manipulation
```{r sum biomass by deployment}

### Total Biomass #############################
# Order Sites and Depths nicely
SOLACE$Depth_Stratum <- factor(as.factor(SOLACE$Depth_Stratum),levels = c("Lmeso", "Meso", "Epi"))
SOLACE$Site <- factor(as.factor(SOLACE$Site), levels = c("SOTS","55S","58S"))

# sum biomass for each deployment
Biomass_deployment <- SOLACE %>% 
  select(Site, daylight,Depth_Stratum, Deployment, Taxa_updated,Acoustic_Category, Abd_Std_nosm3_sp,Weight_Std_gm3_sp) %>%
  dplyr::group_by(Site, daylight, Depth_Stratum,Deployment) %>% 
  dplyr::summarise(StdWt = sum(Weight_Std_gm3_sp), 
                   StdAbd = sum(Abd_Std_nosm3_sp)) %>% 
  dplyr::ungroup() %>% 
  mutate(logwt = log(StdWt))

# average biomass for each treatment by Site/daylight/Depth_Stratum
Biomass_Design <- Biomass_deployment %>% 
  group_by(Site,daylight,Depth_Stratum) %>% 
  summarise(StdWt_avg = mean(StdWt),sd = sd(StdWt),no_reps = n()) %>% 
  ungroup()

#### Acoustic_Category ####################
# sum biomass for each Acoustic_Category within each deployment
Biomass_AC <- SOLACE %>% 
  select(Site, daylight,Depth_Stratum, Deployment, Taxa_updated,Acoustic_Category, Abd_Std_nosm3_sp,Weight_Std_gm3_sp) %>%
  dplyr::group_by(Site, daylight, Depth_Stratum,Deployment,Acoustic_Category) %>% 
  dplyr::summarise(StdWt = sum(Weight_Std_gm3_sp), 
                   StdAbd = sum(Abd_Std_nosm3_sp)) %>% 
  mutate(StdWt = ifelse(daylight %in% "Night", StdWt*-1, StdWt)) %>% 
  dplyr::ungroup() 
# Average biomass for each Acoustic_Category  by Site/daylight/Depth_Stratum
Biomass_Design_AvgAC <- Biomass_AC %>% 
  group_by(Site,daylight,Depth_Stratum,Acoustic_Category) %>% 
  summarise(StdWt_AC = mean(StdWt))

```


##  Plots

### Biomass by Deployment Site/daylight/Depth_Stratum
```{r f.1}, out.width='80%', fig.align='center', fig.cap= "Average biomass by Site, daylight and depth"}
#biomass by shot

Biomass_deployment_daynight <- Biomass_deployment %>% 
   mutate(StdWt = ifelse(daylight %in% "Night", StdWt*-1, StdWt))


deployments<-ggplot(Biomass_deployment_daynight,
       mapping = aes(x = as.factor(Depth_Stratum),
                     y = StdWt, fill = daylight))+
  geom_rect(ymax= -Inf, ymin= 0, xmin=-Inf, xmax=Inf, fill= "grey", alpha= 0.2) +
      scale_fill_manual(values = c("light blue","dark blue")) +
  #scale_fill_brewer()+
geom_point()+
  geom_hline(yintercept=0)+
  coord_flip()+
  facet_grid(Site ~ .,switch = "x")+
  #theme_bw()
 labs(y="Total Average Biomass (g/m^3)", x="Depth Stratum") 
  

deployments
```

### Total Average Biomass by Site/daylight/Depth_Stratum
```{r f.1}, out.width='80%', fig.align='center', fig.cap= "Average biomass by Site, daylight and depth"}
#biomass by shot

Biomass_Desgin_daynight <- Biomass_Design %>% 
   mutate(StdWt = ifelse(daylight %in% "Night", StdWt_avg*-1, StdWt_avg)) %>% 
  mutate(sd = ifelse(daylight %in% "Night", sd*-1, sd)) 


tw_avg<-ggplot(Biomass_Desgin_daynight,
       mapping = aes(x = as.factor(Depth_Stratum),
                     y = StdWt, fill = daylight))+
  geom_rect(ymax= -Inf, ymin= 0, xmin=-Inf, xmax=Inf, fill= "grey", alpha= 0.2) +
      scale_fill_manual(values = c("light blue","dark blue")) +
  #scale_fill_brewer()+
  geom_errorbar(aes(ymin = StdWt - sd, ymax= StdWt + sd),
                width = 0.4, position = position_dodge(0)) +
geom_col()+
  geom_hline(yintercept=0)+
  coord_flip()+
  facet_grid(Site ~ .,switch = "x")+
  #theme_bw()
 labs(y="Total Average Biomass (g/m^3)", x="Depth Stratum") 
  

tw_avg

```

### Sum of Average Biomass for each Acoustic_Category by Site/daylight/Depth_Stratum
```{r sutton code with Acat}
# suttons way
AC_tw_avg <- ggplot(Biomass_Design_AvgAC,
       mapping = aes(x = Depth_Stratum ,y=StdWt_AC, fill = Acoustic_Category))+
     #scale_fill_manual(values = c("purple","orange", "blue","dark blue","light blue","light pink","light green")) +
  geom_rect(ymax= -Inf, ymin= 0, xmin=-Inf, xmax=Inf, fill= "grey", alpha= 0.2) +
  geom_col()+
  #geom_hline(yintercept=0)+
  coord_flip()+
  facet_grid(Site ~.,switch = "x")+  
  labs(x="Depth Stratum", y="Avgerage Biomass g/m^3)") 
AC_tw_avg


# for some reason others don't show up when site labels are on the right side
AC_tw_avg1 <- ggplot(Biomass_Design_AvgAC,
       mapping = aes(x = Depth_Stratum ,y=StdWt_AC, fill = Acoustic_Category))+
     #scale_fill_manual(values = c("purple","orange", "blue","dark blue","light blue", "light pink","light green")) +
  geom_rect(ymax= -Inf, ymin= 0, xmin=-Inf, xmax=Inf, fill= "grey", alpha= 0.2) +
  geom_col()+
  #geom_hline(yintercept=0)+
  coord_flip()+
  facet_grid(Site ~.,switch = "y")+  
  labs(x="Depth Stratum", y="Avgerage Biomass g/m^3)") 

AC_tw_avg1
```


---

### Sum of Average Biomass for Taxa_PLAOS by Site/daylight/Depth_Stratum/Acoustic_Category
```{r Taxa_PLAOS},out.width='100%', fig.align='center', fig.cap= "Average biomass by Site, daylight and depth"}

# sum biomass for each Taxa_PLAOS within each deployment
## data wrangling
Biomass_Taxa_PLAOS <- SOLACE %>% 
  select(Site, daylight,Depth_Stratum, Deployment, Taxa_updated, Acoustic_Category,Taxa_PLAOS, Abd_Std_nosm3_sp,Weight_Std_gm3_sp) %>%
  dplyr::group_by(Site, daylight, Depth_Stratum,Deployment,Acoustic_Category,Taxa_PLAOS) %>% 
  dplyr::summarise(StdWt = sum(Weight_Std_gm3_sp), 
                   StdAbd = sum(Abd_Std_nosm3_sp)) %>% 
  mutate(StdWt = ifelse(daylight %in% "Night", StdWt*-1, StdWt)) %>% 
  dplyr::ungroup() 

# Average biomass for each Taxa_PLAOS  by Site/daylight/Depth_Stratum
Biomass_Design_AvgTP <- Biomass_Taxa_PLAOS %>% 
  group_by(Site,daylight,Depth_Stratum,Acoustic_Category,Taxa_PLAOS) %>% 
  summarise(StdWt_TP = mean(StdWt))

TP_tw_avg <- ggplot(Biomass_Design_AvgTP,
       mapping = aes(x = Depth_Stratum ,y=StdWt_TP, fill = Taxa_PLAOS))+
     #scale_fill_manual(values = c("purple","orange", "blue","dark blue","light blue","light pink","light green")) +
  geom_rect(ymax= -Inf, ymin= 0, xmin=-Inf, xmax=Inf, fill= "grey", alpha= 0.2) +
  geom_col()+
  #geom_hline(yintercept=0)+
  coord_flip()+
  facet_grid(rows= vars(Site), cols= vars(Acoustic_Category), scales = "free") + 
  labs(x="Depth Stratum", y="Avgerage Biomass (g/m^3)") +
  theme(legend.position = "bottom")
  

TP_tw_avg

```
# ANOVA

outliers
```{r outliers}
Biomass_deployment %>%
  group_by(Site,Depth_Stratum) %>%
  identify_outliers(StdWt)
# dont get this
# deployments 8 and 13 are outliers but not extreme. Outliers are not obvious when using Site alone, all 3 factors or Site&daylight
```

normality
``` {r}
Biomass_deployment %>% 
  group_by(Site, daylight, Depth_Stratum) %>% 
  get_summary_stats(StdWt, type = "mean_sd")
```
boxplot
```{r boxplot}
bxp <- ggboxplot(
  Biomass_deployment, x = "daylight", y = "StdWt", 
  color = "Depth_Stratum", palette = "jco", facet.by = "Site"
  )
bxp
```
outliers
```{r outliers}
Biomass_deployment %>%
  group_by(Site, daylight, Depth_Stratum) %>%
  identify_outliers(StdWt)
# dont get this
```


In the QQ plot, as all the points fall approximately along the reference line, we can assume normality. 


This conclusion is supported by the Shapiro-Wilk test, if the p-value is not significant. 
then  can assume normality.
```{r normality}
model  <- lm(StdWt ~ Site*daylight*Depth_Stratum, data = Biomass_deployment)

model2  <- lm(logwt ~ Site*daylight*Depth_Stratum, data = Biomass_deployment)

# Create a QQ plot of residuals
ggqqplot(residuals(model))
# Compute Shapiro-Wilk test of normality
shapiro_test(residuals(model))

# probs not quite normally distributed - should transform

# probs not quite normally distributed - should tranform
```


normality by groups
```{r shapiro test by groups}
Biomass_deployment %>%
  group_by(Site, daylight, Depth_Stratum) %>%
  shapiro_test(StdWt)

```

QQ test
```{r qqtest}
ggqqplot(Biomass_deployment, "StdWt", ggtheme = theme_bw()) +
  facet_grid(Site + daylight ~ Depth_Stratum, labeller = "label_both")
```


homgeneity
```{r levenes}
Biomass_deployment %>% levene_test(StdWt ~ Site*daylight*Depth_Stratum)
# not significant assume homogeneity
```

Anova
```{r anova}
bio.aov <-  Biomass_deployment%>% anova_test(StdWt ~ Depth_Stratum*daylight*Site)
bio.aov
# there was a 3way interaction F(2,22)= 3.04, p = 0.039
```

Post hoc tests
2 way interactions
decide which two variables will form the simple two-way interactions and which variable will act as the third (moderator) variable. 


