---
title: "SOLACE_RMT_analysis"
author: "Caroline Sutton"
date: "28/10/2021"
output:
 html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo=TRUE,
  warning = FALSE,
  message = FALSE,
  results = 'asis',
  fig.align = 'center')

#Load libraries
library(tidyverse)
library(knitr)
library(kableExtra)
library(dplyr)
library(ggplot2)
library(tidyr)
SOLACE <- read_csv("Results/IN2020_V08_CatchComp.csv")

```

---

### Data
SOLACE <- read_csv("Results/IN2020_V08_CatchComp.csv")
```{r SOLACEdata, out.width='100%', echo = T}


knitr::kable(tail(SOLACE, n = 5),caption = "Catch compilation") %>% 
  kableExtra::kable_styling("striped") %>%
  kableExtra::scroll_box(width = "100%")
```

---

### Data manipulation
```{r sum biomass by deployment}

### Total Biomass #############################
# Order Sites and Depths nicely
SOLACE$Depth_Stratum <- factor(as.factor(SOLACE$Depth_Stratum),levels = c("Lmeso", "Meso", "Epi"))
SOLACE$Site <- factor(as.factor(SOLACE$Site), levels = c("SOTS","55S","58S"))

# sum biomass for each deployment
Biomass_deployment <- SOLACE %>% 
  select(Site, daylight,Depth_Stratum, Deployment, Taxa_updated,Acoustic_Category, Abd_Std_nosm3_sp,Weight_Std_gm3_sp) %>%
  dplyr::group_by(Site, daylight, Depth_Stratum,Deployment) %>% 
  dplyr::summarise(StdWt = sum(Weight_Std_gm3_sp), 
                   StdAbd = sum(Abd_Std_nosm3_sp)) %>% 
  dplyr::ungroup() %>% 
  mutate(logwt = log(StdWt))

# average biomass for each treatment by Site/daylight/Depth_Stratum
Biomass_Design <- Biomass_deployment %>% 
  group_by(Site,daylight,Depth_Stratum) %>% 
  summarise(StdWt_avg = mean(StdWt),sd = sd(StdWt),no_reps = n()) %>% 
  ungroup()

#### Acoustic_Category ####################
# sum biomass for each Acoustic_Category within each deployment
Biomass_AC <- SOLACE %>% 
  select(Site, daylight,Depth_Stratum, Deployment, Taxa_updated,Acoustic_Category, Abd_Std_nosm3_sp,Weight_Std_gm3_sp) %>%
  dplyr::group_by(Site, daylight, Depth_Stratum,Deployment,Acoustic_Category) %>% 
  dplyr::summarise(StdWt = sum(Weight_Std_gm3_sp), 
                   StdAbd = sum(Abd_Std_nosm3_sp)) %>% 
  mutate(StdWt = ifelse(daylight %in% "Night", StdWt*-1, StdWt)) %>% 
  dplyr::ungroup() 
# Average biomass for each Acoustic_Category  by Site/daylight/Depth_Stratum
Biomass_Design_AvgAC <- Biomass_AC %>% 
  group_by(Site,daylight,Depth_Stratum,Acoustic_Category) %>% 
  summarise(StdWt_AC = mean(StdWt))

```

---

## Summary Data
Average biomass by Site/daylight/Depth_Stratum
```{r Average Biomass, out.width='100%', echo = T}


knitr::kable(tail(Biomass_Design, n = 18),caption = "Average Biomass") %>% 
  kableExtra::kable_styling("striped") %>%
  kableExtra::scroll_box(width  = "100%")
```

---

##  Plots
### Total Average Biomass by Site/daylight/Depth_Stratum
```{r f.1}, out.width='80%', fig.align='center', fig.cap= "Average biomass by Site, daylight and depth"}
#biomass by shot

Biomass_Desgin_daynight <- Biomass_Design %>% 
   mutate(StdWt = ifelse(daylight %in% "Night", StdWt_avg*-1, StdWt_avg)) %>% 
  mutate(sd = ifelse(daylight %in% "Night", sd*-1, sd)) 


tw_avg<-ggplot(Biomass_Desgin_daynight,
       mapping = aes(x = as.factor(Depth_Stratum),
                     y = StdWt, fill = daylight))+
  geom_rect(ymax= -Inf, ymin= 0, xmin=-Inf, xmax=Inf, fill= "grey", alpha= 0.2) +
      scale_fill_manual(values = c("light blue","dark blue")) +
  #scale_fill_brewer()+
  geom_errorbar(aes(ymin = StdWt - sd, ymax= StdWt + sd),
                width = 0.4, position = position_dodge(0)) +
geom_col()+
  geom_hline(yintercept=0)+
  coord_flip()+
  facet_grid(Site ~ .,switch = "x")+
  #theme_bw()
 labs(y="Total Average Biomass (g/m^3)", x="Depth Stratum") 
  

tw_avg

```

### Sum of Average Biomass for each Acoustic_Category by Site/daylight/Depth_Stratum
```{r sutton code with Acat}
# suttons way
AC_tw_avg <- ggplot(Biomass_Design_AvgAC,
       mapping = aes(x = Depth_Stratum ,y=StdWt_AC, fill = Acoustic_Category))+
     #scale_fill_manual(values = c("purple","orange", "blue","dark blue","light blue","light pink","light green")) +
  geom_rect(ymax= -Inf, ymin= 0, xmin=-Inf, xmax=Inf, fill= "grey", alpha= 0.2) +
  geom_col()+
  #geom_hline(yintercept=0)+
  coord_flip()+
  facet_grid(Site ~.,switch = "x")+  
  labs(x="Depth Stratum", y="Avgerage Biomass g/m^3)") 
AC_tw_avg


# for some reason others don't show up when site labels are on the right side
AC_tw_avg1 <- ggplot(Biomass_Design_AvgAC,
       mapping = aes(x = Depth_Stratum ,y=StdWt_AC, fill = Acoustic_Category))+
     #scale_fill_manual(values = c("purple","orange", "blue","dark blue","light blue", "light pink","light green")) +
  geom_rect(ymax= -Inf, ymin= 0, xmin=-Inf, xmax=Inf, fill= "grey", alpha= 0.2) +
  geom_col()+
  #geom_hline(yintercept=0)+
  coord_flip()+
  facet_grid(Site ~.,switch = "y")+  
  labs(x="Depth Stratum", y="Avgerage Biomass g/m^3)") 

AC_tw_avg1
```


---

### Sum of Average Biomass for Taxa_PLAOS by Site/daylight/Depth_Stratum/Acoustic_Category
```{r Taxa_PLAOS},out.width='100%', fig.align='center', fig.cap= "Average biomass by Site, daylight and depth"}

# sum biomass for each Taxa_PLAOS within each deployment
## data wrangling
Biomass_Taxa_PLAOS <- SOLACE %>% 
  select(Site, daylight,Depth_Stratum, Deployment, Taxa_updated, Acoustic_Category,Taxa_PLAOS, Abd_Std_nosm3_sp,Weight_Std_gm3_sp) %>%
  dplyr::group_by(Site, daylight, Depth_Stratum,Deployment,Acoustic_Category,Taxa_PLAOS) %>% 
  dplyr::summarise(StdWt = sum(Weight_Std_gm3_sp), 
                   StdAbd = sum(Abd_Std_nosm3_sp)) %>% 
  mutate(StdWt = ifelse(daylight %in% "Night", StdWt*-1, StdWt)) %>% 
  dplyr::ungroup() 

# Average biomass for each Taxa_PLAOS  by Site/daylight/Depth_Stratum
Biomass_Design_AvgTP <- Biomass_Taxa_PLAOS %>% 
  group_by(Site,daylight,Depth_Stratum,Acoustic_Category,Taxa_PLAOS) %>% 
  summarise(StdWt_TP = mean(StdWt))

TP_tw_avg <- ggplot(Biomass_Design_AvgTP,
       mapping = aes(x = Depth_Stratum ,y=StdWt_TP, fill = Taxa_PLAOS))+
     #scale_fill_manual(values = c("purple","orange", "blue","dark blue","light blue","light pink","light green")) +
  geom_rect(ymax= -Inf, ymin= 0, xmin=-Inf, xmax=Inf, fill= "grey", alpha= 0.2) +
  geom_col()+
  #geom_hline(yintercept=0)+
  coord_flip()+
  facet_grid(rows= vars(Site), cols= vars(Acoustic_Category), scales = "free") + 
  labs(x="Depth Stratum", y="Avgerage Biomass (g/m^3)") +
  theme(legend.position = "bottom")
  

TP_tw_avg

```
```

