---
title: "Summary data"
author: "sutton"
date: "24/09/2021"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plyr)
library(Rmisc)
library(lattice)
library(tidyr)
library(tidyverse)
library(gridExtra)
library(dplyr)
library(knitr)
library(geosphere)
library(janitor)


SOLACE_M20 <- read_csv("Results/IN2020_V08_CatchComp_Micro20mm.csv")
SOLACE_M15 <- read_csv("Results/IN2020_V08_CatchComp_Micro15mm.csv")
SOLACE <- read_csv("Results/IN2020_V08_CatchComp.csv")
```


#Total Summarised Standardised catch


## Summaries for Micronekton >20mm, using Volume Filtered calculated by ship's speed
```{r total summarised std weight}

# Table of Taxa Groupings
SOLACE <- SOLACE %>% 
  mutate(ACat = ifelse(Taxa_updated == "Pyrosoma atlanticum", "Pyrosome",ACat)) %>% 
  mutate(ACat = ifelse(ACat == "Tunicates", "Salp",ACat))

Taxa_Groupings <- SOLACE %>% 
select(Acoustic_Category,Taxa_Groups,ACat) %>% 
  arrange(Acoustic_Category) %>% 
    distinct(Acoustic_Category,ACat,Taxa_Groups)

S_M20 <- SOLACE %>% 
  filter(ACat == "Siph_physonect" |  AvgL_mm >= 20)
# 
filter(S_M20, ACat == "Tunicates")
SOLACE <- SOLACE %>% 
  mutate(ACat = ifelse(Taxa_updated == "Pyrosoma atlanticum", "Pyrosome","Salp"))
filter(S_M20, Taxa_Groups == "Tunicates")
```

```{r summarising data}
# Total standardised weight
TW20_sp <- S_M20 %>% 
  group_by(Site, daylight,Depth_Stratum,Deployment) %>% 
  filter(Depth_Stratum == "Meso"|Depth_Stratum == "Epi"| Depth_Stratum =="Lmeso") %>% 
  #mutate(Weight_Std_gm3 = ifelse(daylight %in% "Night", Weight_Std_gm3*-1, weight_g)) %>% 
  summarise(TWgm3 = sum(Weight_Std_gm3_sp)) %>% 
  mutate(TWgm3 = ifelse(daylight %in% "Night", TWgm3*-1, TWgm3)) 


# summarise by Acoustic_Category for each deployment
S_M20_Acoustic_Category <-S_M20 %>% 
  group_by(Site,daylight,Depth_Stratum,Deployment, Acoustic_Category) %>% 
  summarise(Nos = sum(nos), Weight_g = sum(weight_g),
            Weight_gm3 = sum(Weight_Std_gm3_gps),Abd_nosm3 =sum(Abd_Std_nosm3_gps))

# summarise by ACat for each deployment
S_M20_ACAt <-S_M20 %>% 
  group_by(Site,daylight,Depth_Stratum,Deployment, ACat) %>% 
  summarise(Nos = sum(nos), Weight_g = sum(weight_g),
            Weight_gm3 = sum(Weight_Std_gm3_gps),Abd_nosm3 =sum(Abd_Std_nosm3_gps))

# summarise by Taxa_Groups for each deployment
S_M20_Taxa_Groups <-S_M20 %>% 
  group_by(Site,daylight,Depth_Stratum,Deployment, Taxa_Groups) %>% 
  summarise(Nos = sum(nos), Weight_g = sum(weight_g),
            Weight_gm3 = sum(Weight_Std_gm3_gps),Abd_nosm3 =sum(Abd_Std_nosm3_gps))

# summarise by Taxa_updated for each deployment
S_M20_Taxa_updated <-S_M20 %>% 
  group_by(Site,daylight,Depth_Stratum,Deployment, Taxa_updated) %>% 
  summarise(Nos = sum(nos), Weight_g = sum(weight_g),
            Weight_gm3 = sum(Weight_Std_gm3_gps),Abd_nosm3 =sum(Abd_Std_nosm3_gps))


## TW by Micro_all and VF by gps
# TW_std_gps <- SOLACE %>% 
#   group_by(Site, daylight,Depth_Stratum,Deployment) %>% 
#   filter(Depth_Stratum == "Meso"|Depth_Stratum == "Epi"| Depth_Stratum =="Lmeso") %>% 
#   #mutate(Weight_Std_gm3 = ifelse(daylight %in% "Night", Weight_Std_gm3*-1, weight_g)) %>% 
#   summarise(TWgm3 = sum(Weight_Std_gm3_gps)) %>% 
#   mutate(TWgm3 = ifelse(daylight %in% "Night", TWgm3*-1, TWgm3)) 
# 
# unique(SOLACE$ACat)

# TW_std_bigger20mm <- SOLACE %>% 
#   filter(AvgL_mm >= 20) %>% 
#   group_by(Site, daylight,Depth_Stratum,Deployment) %>% 
#   filter(Depth_Stratum == "Meso"|Depth_Stratum == "Epi"| Depth_Stratum =="Lmeso") %>% 
#   #mutate(Weight_Std_gm3 = ifelse(daylight %in% "Night", Weight_Std_gm3*-1, weight_g)) %>% 
#   summarise(TWgm3 = sum(Weight_Std_gm3_sp)) %>% 
#   mutate(TWgm3 = ifelse(daylight %in% "Night", TWgm3*-1, TWgm3)) 

```


# Create Plot
# TW standardised with speed of net
```{r Tottal Weight}
TW20_sp$Depth_Stratum <- factor(as.factor(TW20_sp$Depth_Stratum),levels = c("Lmeso", "Meso", "Epi"))
TW20_sp$Site <- factor(as.factor(TW20_sp$Site), levels = c("SOTS","55S","58S"))
TW20_sp_1 <- TW20_sp %>%
  group_by(Site,daylight,Depth_Stratum) %>%
 #mutate(TW_std = TW_std*1000) %>%
  summarise(n(),TW20_sp = round(mean(TWgm3,na.rm = TRUE),digits = 2),
            sd = round(sd(TWgm3,na.rm = TRUE),digits = 2)
            )
TW_sp <-ggplot(TW20_sp_1,
       mapping = aes(x = as.factor(Depth_Stratum),
                     y = TW20_sp, fill = daylight))+
  scale_fill_brewer()+
  geom_errorbar(aes(ymin = TW20_sp - sd, ymax= TW20_sp + sd),
                width = 0.4, position = position_dodge(0)) +
geom_col()+
  coord_flip()+
  facet_grid(~Site)+
  theme_bw()
TW_sp
ggsave(TW_sp,filename = "figures/tw_sp_M20.jpg")


# # TW standardised with gps of net
# TW_std_gps$Depth_Stratum <- factor(as.factor(TW_std_gps$Depth_Stratum),levels = c("Lmeso", "Meso", "Epi"))
# TW_std_gps$Site <- factor(as.factor(TW_std_gps$Site), levels = c("SOTS","55S","58S"))
# TW_std_gps_1 <- TW_std_gps %>%
#   group_by(Site,daylight,Depth_Stratum) %>%
#  #mutate(TW_std = TW_std*1000) %>%
#   summarise(n(),TW_std_gps = round(mean(TWgm3,na.rm = TRUE),digits = 2),
#             sd = round(sd(TWgm3,na.rm = TRUE),digits = 2)
#             )
# TWgps<-ggplot(TW_std_gps_1,
#        mapping = aes(x = as.factor(Depth_Stratum),
#                      y = TW_std_gps, fill = daylight))+
#   scale_fill_brewer()+
#   geom_errorbar(aes(ymin = TW_std_gps - sd, ymax= TW_std_gps + sd),
#                 width = 0.4, position = position_dodge(0)) +
# geom_col()+
#   coord_flip()+
#   facet_grid(~Site)+
#   theme_bw()
# 
# TWgps 
# ggsave(TWgps,filename = "Results/tw_gps.jpg")
```

# Total Weight Summary using SummarySE
```{r total weight summary}
# Summary Using SummarySE 
## still based on "ccomp_6_SumShot"
TW20_sp_summary <- summarySE(TW20_sp, measurevar = "TWgm3", groupvars = c("Site", "daylight", "Depth_Stratum"))
TW20_sp_plot <- ggplot(TW20_sp_summary,
                     mapping = aes(x = as.factor(Depth_Stratum),
                                   y = TWgm3, fill = daylight))+
  #scale_fill_brewer()+
  geom_errorbar(aes(ymin = TWgm3 - sd, ymax= TWgm3 + sd,colour = daylight),
                width = 0.4, position = position_dodge(0)) +
  xlab("Depth Stratum")+
  ylab("TW20 Standardised wet weight (g/m^3)")+
  #scale_x_discrete(limits = c(-0.9,0.9))+
  scale_fill_manual(values=c("light blue","dark blue"))+
  scale_colour_manual(values =c("light blue", "dark blue"))+
  geom_col()+
  coord_flip()+
  facet_grid(~Site)+
  theme_bw()
TW20_sp_plot
plot(TW20_sp_plot)
ggsave("figures/Paper/TW20_sp.jpg")


# TW_summary_gps <- summarySE(TW_std_gps, measurevar = "TWgm3", groupvars = c("Site", "daylight", "Depth_Stratum"))
# TWSum_gps_plot <- ggplot(TW_summary_gps,
#                      mapping = aes(x = as.factor(Depth_Stratum),
#                                    y = TWgm3, fill = daylight))+
#   #scale_fill_brewer()+
#   geom_errorbar(aes(ymin = TWgm3 - sd, ymax= TWgm3 + sd,colour = daylight),
#                 width = 0.4, position = position_dodge(0)) +
#   xlab("Depth Stratum")+
#   ylab("Standardised wet weight (g/m^3)")+
#   #scale_x_discrete(limits = c(-0.9,0.9))+
#   scale_fill_manual(values=c("light blue","dark blue"))+
#   scale_colour_manual(values =c("light blue", "dark blue"))+
#   geom_col()+
#   coord_flip()+
#   facet_grid(~Site)+
#   theme_bw()
# TWSum_gps_plot
# plot(TWSum_gps_plot)
# ggsave("figures/TWeight_gps_gm3.jpg")
```


# Percent Contribution
```{r percent contribution biomass by site}

# include only the replicated sites
SOLACE_M20_1 <- S_M20 %>% 
  filter(Site == "55S" | Site == "58S" |Site == "SOTS") %>% 
  filter(Depth_Stratum =="Meso" | Depth_Stratum == "Epi"|Depth_Stratum=="Lmeso") %>%   drop_na(Site)

distinct(SOLACE_M20,Depth_Stratum)
distinct(SOLACE_M20_1,Depth_Stratum)

SOLACE_M20_1 <- SOLACE_M20 %>% 
  select(Site,Acoustic_Category,Taxa_updated,weight_g) %>% 
  group_by(Site,Taxa_updated) %>% 
  summarise(weight = sum(weight_g)) %>% 
  arrange(Site,-weight) %>% 
  mutate(cumsum = cumsum(weight)) %>% 
  mutate(cumpercent = cumsum/sum(weight)) %>% 
  mutate(percent =round(weight/sum(weight),2)) 

write.csv(SOLACE_M20_1,"figures/Paper/CumPercent.csv")
# 
 S_M20 %>% filter(Acoustic_Category == "FnGB")
```


# Plots by Acoustic_Groups 

```{r Acoustic_Groups}

# G_nGB
Ind_Acoustic_Category <- S_M20_Acoustic_Category%>% 
  group_by(Site,daylight,Depth_Stratum,Deployment) %>% 
  filter(Acoustic_Category=="G_nGB") %>% 
 # filter(Taxa_updated =="Lampanyctus australis") %>% 
  filter(Depth_Stratum == "Meso"|Depth_Stratum == "Epi"| Depth_Stratum =="Lmeso") %>% 
  #mutate(Weight_Std_gm3 = ifelse(daylight %in% "Night", Weight_Std_gm3*-1, weight_g)) %>% 
  summarise(TWgm3 = sum(Weight_gm3)) %>% 
  mutate(TWgm3 = ifelse(daylight %in% "Night", TWgm3*-1, TWgm3)) %>% 
  group_by(Site, daylight,Depth_Stratum) %>% 
  summarise(TWgm3_avg = mean(TWgm3),n(),sd=sd(TWgm3,na.rm = TRUE))
Ind_Acoustic_Category$Site <- factor(as.factor(Ind_Acoustic_Category$Site), levels = c("SOTS","55S","58S"))
Ind_Acoustic_Category$Depth_Stratum <- factor(as.factor(Ind_Acoustic_Category$Depth_Stratum),levels = c("Lmeso", "Meso", "Epi"))
Ind_Acoustic_Category_plot <- ggplot(Ind_Acoustic_Category,
                     mapping = aes(x = as.factor(Depth_Stratum),
                                   y = TWgm3_avg, fill = daylight))+
    geom_errorbar(aes(ymin = TWgm3_avg - sd, ymax= TWgm3_avg + sd, colour = factor(daylight)),
                width = 0.3, position = position_dodge(0)) +
  #geom_errorbar(aes(ymin=y, ymax=y_upper.error), colour="blue", width = 0.1) +
  #geom_errorbar(aes(ymin=y_lower.error, ymax=y), colour="red", width = 0.1) +
  xlab("Depth Stratum")+
  ylab("G_nGB: Standardised wet weight (g/m^3)")+
  #scale_x_discrete(limits = c(-0.9,0.9))+
  scale_colour_manual("daylight",values=c("light blue","dark blue"))+
  scale_fill_manual("daylight",values=c("light blue","dark blue"))+
  geom_col()+
  coord_flip()+
  facet_grid(~Site)+
  theme_bw()
plot(Ind_Acoustic_Category_plot)
ggsave("figures/Paper/G_nGB.jpg")
```




G_GB
```{r G_GB}

# G_GB
Ind_Acoustic_Category <- S_M20_Acoustic_Category%>% 
  group_by(Site,daylight,Depth_Stratum,Deployment) %>% 
  filter(Acoustic_Category=="G_GB") %>% 
 # filter(Taxa_updated =="Lampanyctus australis") %>% 
  filter(Depth_Stratum == "Meso"|Depth_Stratum == "Epi"| Depth_Stratum =="Lmeso") %>% 
  #mutate(Weight_Std_gm3 = ifelse(daylight %in% "Night", Weight_Std_gm3*-1, weight_g)) %>% 
  summarise(TWgm3 = sum(Weight_gm3)) %>% 
  mutate(TWgm3 = ifelse(daylight %in% "Night", TWgm3*-1, TWgm3)) %>% 
  group_by(Site, daylight,Depth_Stratum) %>% 
  summarise(TWgm3_avg = mean(TWgm3),n(),sd=sd(TWgm3,na.rm = TRUE))
Ind_Acoustic_Category$Site <- factor(as.factor(Ind_Acoustic_Category$Site), levels = c("SOTS","55S","58S"))
Ind_Acoustic_Category$Depth_Stratum <- factor(as.factor(Ind_Acoustic_Category$Depth_Stratum),levels = c("Lmeso", "Meso", "Epi"))
Ind_Acoustic_Category_plot <- ggplot(Ind_Acoustic_Category,
                     mapping = aes(x = as.factor(Depth_Stratum),
                                   y = TWgm3_avg, fill = daylight))+
    geom_errorbar(aes(ymin = TWgm3_avg - sd, ymax= TWgm3_avg + sd, colour = factor(daylight)),
                width = 0.3, position = position_dodge(0)) +
  #geom_errorbar(aes(ymin=y, ymax=y_upper.error), colour="blue", width = 0.1) +
  #geom_errorbar(aes(ymin=y_lower.error, ymax=y), colour="red", width = 0.1) +
  xlab("Depth Stratum")+
  ylab("G_GB: Standardised wet weight (g/m^3)")+
  #scale_x_discrete(limits = c(-0.9,0.9))+
  scale_colour_manual("daylight",values=c("light blue","dark blue"))+
  scale_fill_manual("daylight",values=c("light blue","dark blue"))+
  geom_col()+
  coord_flip()+
  facet_grid(~Site)+
  theme_bw()
plot(Ind_Acoustic_Category_plot)
ggsave("figures/Paper/G_GB.jpg")

```

FGB
```{r FGB}

# FGB
Ind_Acoustic_Category <- S_M20_Acoustic_Category%>% 
  group_by(Site,daylight,Depth_Stratum,Deployment) %>% 
  filter(Acoustic_Category=="FGB") %>% 
 # filter(Taxa_updated =="Lampanyctus australis") %>% 
  filter(Depth_Stratum == "Meso"|Depth_Stratum == "Epi"| Depth_Stratum =="Lmeso") %>% 
  #mutate(Weight_Std_gm3 = ifelse(daylight %in% "Night", Weight_Std_gm3*-1, weight_g)) %>% 
  summarise(TWgm3 = sum(Weight_gm3)) %>% 
  mutate(TWgm3 = ifelse(daylight %in% "Night", TWgm3*-1, TWgm3)) %>% 
  group_by(Site, daylight,Depth_Stratum) %>% 
  summarise(TWgm3_avg = mean(TWgm3),n(),sd=sd(TWgm3,na.rm = TRUE))
Ind_Acoustic_Category$Site <- factor(as.factor(Ind_Acoustic_Category$Site), levels = c("SOTS","55S","58S"))
Ind_Acoustic_Category$Depth_Stratum <- factor(as.factor(Ind_Acoustic_Category$Depth_Stratum),levels = c("Lmeso", "Meso", "Epi"))
Ind_Acoustic_Category_plot <- ggplot(Ind_Acoustic_Category,
                     mapping = aes(x = as.factor(Depth_Stratum),
                                   y = TWgm3_avg, fill = daylight))+
    geom_errorbar(aes(ymin = TWgm3_avg - sd, ymax= TWgm3_avg + sd, colour = factor(daylight)),
                width = 0.3, position = position_dodge(0)) +
  #geom_errorbar(aes(ymin=y, ymax=y_upper.error), colour="blue", width = 0.1) +
  #geom_errorbar(aes(ymin=y_lower.error, ymax=y), colour="red", width = 0.1) +
  xlab("Depth Stratum")+
  ylab("FGB: Standardised wet weight (g/m^3)")+
  #scale_x_discrete(limits = c(-0.9,0.9))+
  scale_colour_manual("daylight",values=c("light blue","dark blue"))+
  scale_fill_manual("daylight",values=c("light blue","dark blue"))+
  geom_col()+
  coord_flip()+
  facet_grid(~Site)+
  theme_bw()
plot(Ind_Acoustic_Category_plot)
ggsave("figures/Paper/FGB.jpg")

```
F
```{r FGB}

# F
Ind_Acoustic_Category <- S_M20_Acoustic_Category%>% 
  group_by(Site,daylight,Depth_Stratum,Deployment) %>% 
  filter(Acoustic_Category=="F") %>% 
 # filter(Taxa_updated =="Lampanyctus australis") %>% 
  filter(Depth_Stratum == "Meso"|Depth_Stratum == "Epi"| Depth_Stratum =="Lmeso") %>% 
  #mutate(Weight_Std_gm3 = ifelse(daylight %in% "Night", Weight_Std_gm3*-1, weight_g)) %>% 
  summarise(TWgm3 = sum(Weight_gm3)) %>% 
  mutate(TWgm3 = ifelse(daylight %in% "Night", TWgm3*-1, TWgm3)) %>% 
  group_by(Site, daylight,Depth_Stratum) %>% 
  summarise(TWgm3_avg = mean(TWgm3),n(),sd=sd(TWgm3,na.rm = TRUE))
Ind_Acoustic_Category$Site <- factor(as.factor(Ind_Acoustic_Category$Site), levels = c("SOTS","55S","58S"))
Ind_Acoustic_Category$Depth_Stratum <- factor(as.factor(Ind_Acoustic_Category$Depth_Stratum),levels = c("Lmeso", "Meso", "Epi"))
Ind_Acoustic_Category_plot <- ggplot(Ind_Acoustic_Category,
                     mapping = aes(x = as.factor(Depth_Stratum),
                                   y = TWgm3_avg, fill = daylight))+
    geom_errorbar(aes(ymin = TWgm3_avg - sd, ymax= TWgm3_avg + sd, colour = factor(daylight)),
                width = 0.3, position = position_dodge(0)) +
  #geom_errorbar(aes(ymin=y, ymax=y_upper.error), colour="blue", width = 0.1) +
  #geom_errorbar(aes(ymin=y_lower.error, ymax=y), colour="red", width = 0.1) +
  xlab("Depth Stratum")+
  ylab("F: Standardised wet weight (g/m^3)")+
  #scale_x_discrete(limits = c(-0.9,0.9))+
  scale_colour_manual("daylight",values=c("light blue","dark blue"))+
  scale_fill_manual("daylight",values=c("light blue","dark blue"))+
  geom_col()+
  coord_flip()+
  facet_grid(~Site)+
  theme_bw()
plot(Ind_Acoustic_Category_plot)
ggsave("figures/Paper/F.jpg")

```
Crustaceans
```{r Crustaceans}

# Crustaceans
Ind_Acoustic_Category <- S_M20_Acoustic_Category%>% 
  group_by(Site,daylight,Depth_Stratum,Deployment) %>% 
  filter(Acoustic_Category=="Crustaceans") %>% 
 # filter(Taxa_updated =="Lampanyctus australis") %>% 
  filter(Depth_Stratum == "Meso"|Depth_Stratum == "Epi"| Depth_Stratum =="Lmeso") %>% 
  #mutate(Weight_Std_gm3 = ifelse(daylight %in% "Night", Weight_Std_gm3*-1, weight_g)) %>% 
  summarise(TWgm3 = sum(Weight_gm3)) %>% 
  mutate(TWgm3 = ifelse(daylight %in% "Night", TWgm3*-1, TWgm3)) %>% 
  group_by(Site, daylight,Depth_Stratum) %>% 
  summarise(TWgm3_avg = mean(TWgm3),n(),sd=sd(TWgm3,na.rm = TRUE))
Ind_Acoustic_Category$Site <- factor(as.factor(Ind_Acoustic_Category$Site), levels = c("SOTS","55S","58S"))
Ind_Acoustic_Category$Depth_Stratum <- factor(as.factor(Ind_Acoustic_Category$Depth_Stratum),levels = c("Lmeso", "Meso", "Epi"))
Ind_Acoustic_Category_plot <- ggplot(Ind_Acoustic_Category,
                     mapping = aes(x = as.factor(Depth_Stratum),
                                   y = TWgm3_avg, fill = daylight))+
    geom_errorbar(aes(ymin = TWgm3_avg - sd, ymax= TWgm3_avg + sd, colour = factor(daylight)),
                width = 0.3, position = position_dodge(0)) +
  #geom_errorbar(aes(ymin=y, ymax=y_upper.error), colour="blue", width = 0.1) +
  #geom_errorbar(aes(ymin=y_lower.error, ymax=y), colour="red", width = 0.1) +
  xlab("Depth Stratum")+
  ylab("Crustaceans: Standardised wet weight (g/m^3)")+
  #scale_x_discrete(limits = c(-0.9,0.9))+
  scale_colour_manual("daylight",values=c("light blue","dark blue"))+
  scale_fill_manual("daylight",values=c("light blue","dark blue"))+
  geom_col()+
  coord_flip()+
  facet_grid(~Site)+
  theme_bw()
plot(Ind_Acoustic_Category_plot)
ggsave("figures/Paper/Crustaceans.jpg")

```
Cephalopod
```{r Cephalopod}

# Cephalopod
Ind_Acoustic_Category <- S_M20_Acoustic_Category%>% 
  group_by(Site,daylight,Depth_Stratum,Deployment) %>% 
  filter(Acoustic_Category=="Cephalopod") %>% 
 # filter(Taxa_updated =="Lampanyctus australis") %>% 
  filter(Depth_Stratum == "Meso"|Depth_Stratum == "Epi"| Depth_Stratum =="Lmeso") %>% 
  #mutate(Weight_Std_gm3 = ifelse(daylight %in% "Night", Weight_Std_gm3*-1, weight_g)) %>% 
  summarise(TWgm3 = sum(Weight_gm3)) %>% 
  mutate(TWgm3 = ifelse(daylight %in% "Night", TWgm3*-1, TWgm3)) %>% 
  group_by(Site, daylight,Depth_Stratum) %>% 
  summarise(TWgm3_avg = mean(TWgm3),n(),sd=sd(TWgm3,na.rm = TRUE))
Ind_Acoustic_Category$Site <- factor(as.factor(Ind_Acoustic_Category$Site), levels = c("SOTS","55S","58S"))
Ind_Acoustic_Category$Depth_Stratum <- factor(as.factor(Ind_Acoustic_Category$Depth_Stratum),levels = c("Lmeso", "Meso", "Epi"))
Ind_Acoustic_Category_plot <- ggplot(Ind_Acoustic_Category,
                     mapping = aes(x = as.factor(Depth_Stratum),
                                   y = TWgm3_avg, fill = daylight))+
    geom_errorbar(aes(ymin = TWgm3_avg - sd, ymax= TWgm3_avg + sd, colour = factor(daylight)),
                width = 0.3, position = position_dodge(0)) +
  #geom_errorbar(aes(ymin=y, ymax=y_upper.error), colour="blue", width = 0.1) +
  #geom_errorbar(aes(ymin=y_lower.error, ymax=y), colour="red", width = 0.1) +
  xlab("Depth Stratum")+
  ylab("Cephalopod: Standardised wet weight (g/m^3)")+
  #scale_x_discrete(limits = c(-0.9,0.9))+
  scale_colour_manual("daylight",values=c("light blue","dark blue"))+
  scale_fill_manual("daylight",values=c("light blue","dark blue"))+
  geom_col()+
  coord_flip()+
  facet_grid(~Site)+
  theme_bw()
plot(Ind_Acoustic_Category_plot)
ggsave("figures/Paper/Cephalopod.jpg")

```

other
```{r Other}

# other
Ind_Acoustic_Category <- S_M20_Acoustic_Category%>% 
  group_by(Site,daylight,Depth_Stratum,Deployment) %>% 
  filter(Acoustic_Category=="other") %>% 
 # filter(Taxa_updated =="Lampanyctus australis") %>% 
  filter(Depth_Stratum == "Meso"|Depth_Stratum == "Epi"| Depth_Stratum =="Lmeso") %>% 
  #mutate(Weight_Std_gm3 = ifelse(daylight %in% "Night", Weight_Std_gm3*-1, weight_g)) %>% 
  summarise(TWgm3 = sum(Weight_gm3)) %>% 
  mutate(TWgm3 = ifelse(daylight %in% "Night", TWgm3*-1, TWgm3)) %>% 
  group_by(Site, daylight,Depth_Stratum) %>% 
  summarise(TWgm3_avg = mean(TWgm3),n(),sd=sd(TWgm3,na.rm = TRUE))
Ind_Acoustic_Category$Site <- factor(as.factor(Ind_Acoustic_Category$Site), levels = c("SOTS","55S","58S"))
Ind_Acoustic_Category$Depth_Stratum <- factor(as.factor(Ind_Acoustic_Category$Depth_Stratum),levels = c("Lmeso", "Meso", "Epi"))
Ind_Acoustic_Category_plot <- ggplot(Ind_Acoustic_Category,
                     mapping = aes(x = as.factor(Depth_Stratum),
                                   y = TWgm3_avg, fill = daylight))+
    geom_errorbar(aes(ymin = TWgm3_avg - sd, ymax= TWgm3_avg + sd, colour = factor(daylight)),
                width = 0.3, position = position_dodge(0)) +
  #geom_errorbar(aes(ymin=y, ymax=y_upper.error), colour="blue", width = 0.1) +
  #geom_errorbar(aes(ymin=y_lower.error, ymax=y), colour="red", width = 0.1) +
  xlab("Depth Stratum")+
  ylab("other: Standardised wet weight (g/m^3)")+
  #scale_x_discrete(limits = c(-0.9,0.9))+
  scale_colour_manual("daylight",values=c("light blue","dark blue"))+
  scale_fill_manual("daylight",values=c("light blue","dark blue"))+
  geom_col()+
  coord_flip()+
  facet_grid(~Site)+
  theme_bw()
plot(Ind_Acoustic_Category_plot)
ggsave("figures/Paper/other.jpg")

```



# Summary by Taxa_Groups
chaetognaths
```{r chaetognaths}

# chaetognaths
Ind_Taxa_Groups <- S_M20_Taxa_Groups%>% 
  group_by(Site,daylight,Depth_Stratum,Deployment) %>% 
  filter(Taxa_Groups=="chaetognaths") %>% 
 # filter(Taxa_updated =="Lampanyctus australis") %>% 
  filter(Depth_Stratum == "Meso"|Depth_Stratum == "Epi"| Depth_Stratum =="Lmeso") %>% 
  #mutate(Weight_Std_gm3 = ifelse(daylight %in% "Night", Weight_Std_gm3*-1, weight_g)) %>% 
  summarise(TWgm3 = sum(Weight_gm3)) %>% 
  mutate(TWgm3 = ifelse(daylight %in% "Night", TWgm3*-1, TWgm3)) %>% 
  group_by(Site, daylight,Depth_Stratum) %>% 
  summarise(TWgm3_avg = mean(TWgm3),n(),sd=sd(TWgm3,na.rm = TRUE))
Ind_Acoustic_Category$Site <- factor(as.factor(Ind_Acoustic_Category$Site), levels = c("SOTS","55S","58S"))
Ind_Acoustic_Category$Depth_Stratum <- factor(as.factor(Ind_Acoustic_Category$Depth_Stratum),levels = c("Lmeso", "Meso", "Epi"))
Ind_Taxa_Group_plot <- ggplot(Ind_Acoustic_Category,
                     mapping = aes(x = as.factor(Depth_Stratum),
                                   y = TWgm3_avg, fill = daylight))+
    geom_errorbar(aes(ymin = TWgm3_avg - sd, ymax= TWgm3_avg + sd, colour = factor(daylight)),
                width = 0.3, position = position_dodge(0)) +
  #geom_errorbar(aes(ymin=y, ymax=y_upper.error), colour="blue", width = 0.1) +
  #geom_errorbar(aes(ymin=y_lower.error, ymax=y), colour="red", width = 0.1) +
  xlab("Depth Stratum")+
  ylab("chaetognaths: Standardised wet weight (g/m^3)")+
  #scale_x_discrete(limits = c(-0.9,0.9))+
  scale_colour_manual("daylight",values=c("light blue","dark blue"))+
  scale_fill_manual("daylight",values=c("light blue","dark blue"))+
  geom_col()+
  coord_flip()+
  facet_grid(~Site)+
  theme_bw()
plot(Ind_Taxa_Group_plot)
ggsave("figures/Paper/chaetognaths.jpg")
```

Tunicates
```{r Tunicates}

# chaetognaths
Ind_Taxa_Groups <- S_M20_Taxa_Groups%>% 
  group_by(Site,daylight,Depth_Stratum,Deployment) %>% 
  filter(Taxa_Groups=="Tunicates") %>% 
  filter(Depth_Stratum == "Meso"|Depth_Stratum == "Epi"| Depth_Stratum =="Lmeso") %>% 
  #mutate(Weight_Std_gm3 = ifelse(daylight %in% "Night", Weight_Std_gm3*-1, weight_g)) %>% 
  summarise(TWgm3 = sum(Weight_gm3)) %>% 
  mutate(TWgm3 = ifelse(daylight %in% "Night", TWgm3*-1, TWgm3)) %>% 
  group_by(Site, daylight,Depth_Stratum) %>% 
  summarise(TWgm3_avg = mean(TWgm3),n(),sd=sd(TWgm3,na.rm = TRUE))
Ind_Acoustic_Category$Site <- factor(as.factor(Ind_Acoustic_Category$Site), levels = c("SOTS","55S","58S"))
Ind_Acoustic_Category$Depth_Stratum <- factor(as.factor(Ind_Acoustic_Category$Depth_Stratum),levels = c("Lmeso", "Meso", "Epi"))
Ind_Taxa_Group_plot <- ggplot(Ind_Acoustic_Category,
                     mapping = aes(x = as.factor(Depth_Stratum),
                                   y = TWgm3_avg, fill = daylight))+
    geom_errorbar(aes(ymin = TWgm3_avg - sd, ymax= TWgm3_avg + sd, colour = factor(daylight)),
                width = 0.3, position = position_dodge(0)) +
  #geom_errorbar(aes(ymin=y, ymax=y_upper.error), colour="blue", width = 0.1) +
  #geom_errorbar(aes(ymin=y_lower.error, ymax=y), colour="red", width = 0.1) +
  xlab("Depth Stratum")+
  ylab("Tunicates: Standardised wet weight (g/m^3)")+
  #scale_x_discrete(limits = c(-0.9,0.9))+
  scale_colour_manual("daylight",values=c("light blue","dark blue"))+
  scale_fill_manual("daylight",values=c("light blue","dark blue"))+
  geom_col()+
  coord_flip()+
  facet_grid(~Site)+
  theme_bw()
plot(Ind_Taxa_Group_plot)
ggsave("figures/Paper/Tunicates.jpg")
```

# summary by ACat
krill
```{r krill}

# krill
Ind_S_M20_ACAt <- S_M20_ACAt%>% 
  group_by(Site,daylight,Depth_Stratum,Deployment) %>% 
  filter(ACat=="Krill") %>% 
 # filter(Taxa_updated =="Lampanyctus australis") %>% 
  filter(Depth_Stratum == "Meso"|Depth_Stratum == "Epi"| Depth_Stratum =="Lmeso") %>% 
  #mutate(Weight_Std_gm3 = ifelse(daylight %in% "Night", Weight_Std_gm3*-1, weight_g)) %>% 
  summarise(TWgm3 = sum(Weight_gm3)) %>% 
  mutate(TWgm3 = ifelse(daylight %in% "Night", TWgm3*-1, TWgm3)) %>% 
  group_by(Site, daylight,Depth_Stratum) %>% 
  summarise(TWgm3_avg = mean(TWgm3),n(),sd=sd(TWgm3,na.rm = TRUE))
Ind_S_M20_ACAt$Site <- factor(as.factor(Ind_S_M20_ACAt$Site), levels = c("SOTS","55S","58S"))
Ind_S_M20_ACAt$Depth_Stratum <- factor(as.factor(Ind_S_M20_ACAt$Depth_Stratum),levels = c("Lmeso", "Meso", "Epi"))
Ind_S_M20_ACAt_plot <- ggplot(Ind_S_M20_ACAt,
                     mapping = aes(x = as.factor(Depth_Stratum),
                                   y = TWgm3_avg, fill = daylight))+
    geom_errorbar(aes(ymin = TWgm3_avg - sd, ymax= TWgm3_avg + sd, colour = factor(daylight)),
                width = 0.3, position = position_dodge(0)) +
  #geom_errorbar(aes(ymin=y, ymax=y_upper.error), colour="blue", width = 0.1) +
  #geom_errorbar(aes(ymin=y_lower.error, ymax=y), colour="red", width = 0.1) +
  xlab("Depth Stratum")+
  ylab("Krill: Standardised wet weight (g/m^3)")+
  #scale_x_discrete(limits = c(-0.9,0.9))+
  scale_colour_manual("daylight",values=c("light blue","dark blue"))+
  scale_fill_manual("daylight",values=c("light blue","dark blue"))+
  geom_col()+
  coord_flip()+
  facet_grid(~Site)+
  theme_bw()
plot(Ind_S_M20_ACAt_plot)
ggsave("figures/Paper/krill.jpg")



```


Prawn
```{r prawn}

# Prawn
Ind_S_M20_ACAt <- S_M20_ACAt%>% 
  group_by(Site,daylight,Depth_Stratum,Deployment) %>% 
  filter(ACat=="Prawn") %>% 
  filter(Depth_Stratum == "Meso"|Depth_Stratum == "Epi"| Depth_Stratum =="Lmeso") %>% 
  #mutate(Weight_Std_gm3 = ifelse(daylight %in% "Night", Weight_Std_gm3*-1, weight_g)) %>% 
  summarise(TWgm3 = sum(Weight_gm3)) %>% 
  mutate(TWgm3 = ifelse(daylight %in% "Night", TWgm3*-1, TWgm3)) %>% 
  group_by(Site, daylight,Depth_Stratum) %>% 
  summarise(TWgm3_avg = mean(TWgm3),n(),sd=sd(TWgm3,na.rm = TRUE))
Ind_S_M20_ACAt$Site <- factor(as.factor(Ind_S_M20_ACAt$Site), levels = c("SOTS","55S","58S"))
Ind_S_M20_ACAt$Depth_Stratum <- factor(as.factor(Ind_S_M20_ACAt$Depth_Stratum),levels = c("Lmeso", "Meso", "Epi"))
Ind_S_M20_ACAt_plot <- ggplot(Ind_S_M20_ACAt,
                     mapping = aes(x = as.factor(Depth_Stratum),
                                   y = TWgm3_avg, fill = daylight))+
    geom_errorbar(aes(ymin = TWgm3_avg - sd, ymax= TWgm3_avg + sd, colour = factor(daylight)),
                width = 0.3, position = position_dodge(0)) +
  #geom_errorbar(aes(ymin=y, ymax=y_upper.error), colour="blue", width = 0.1) +
  #geom_errorbar(aes(ymin=y_lower.error, ymax=y), colour="red", width = 0.1) +
  xlab("Depth Stratum")+
  ylab("Prawn: Standardised wet weight (g/m^3)")+
  #scale_x_discrete(limits = c(-0.9,0.9))+
  scale_colour_manual("daylight",values=c("light blue","dark blue"))+
  scale_fill_manual("daylight",values=c("light blue","dark blue"))+
  geom_col()+
  coord_flip()+
  facet_grid(~Site)+
  theme_bw()
plot(Ind_S_M20_ACAt_plot)
ggsave("figures/Paper/Prawn.jpg")

```

ctenophore
```{r practenophorewn}

# Prawn
Ind_S_M20_ACAt <- S_M20_ACAt%>% 
  group_by(Site,daylight,Depth_Stratum,Deployment) %>% 
  filter(ACat=="Ctenophore") %>% 
  filter(Depth_Stratum == "Meso"|Depth_Stratum == "Epi"| Depth_Stratum =="Lmeso") %>% 
  #mutate(Weight_Std_gm3 = ifelse(daylight %in% "Night", Weight_Std_gm3*-1, weight_g)) %>% 
  summarise(TWgm3 = sum(Weight_gm3)) %>% 
  mutate(TWgm3 = ifelse(daylight %in% "Night", TWgm3*-1, TWgm3)) %>% 
  group_by(Site, daylight,Depth_Stratum) %>% 
  summarise(TWgm3_avg = mean(TWgm3),n(),sd=sd(TWgm3,na.rm = TRUE))
Ind_S_M20_ACAt$Site <- factor(as.factor(Ind_S_M20_ACAt$Site), levels = c("SOTS","55S","58S"))
Ind_S_M20_ACAt$Depth_Stratum <- factor(as.factor(Ind_S_M20_ACAt$Depth_Stratum),levels = c("Lmeso", "Meso", "Epi"))
Ind_S_M20_ACAt_plot <- ggplot(Ind_S_M20_ACAt,
                     mapping = aes(x = as.factor(Depth_Stratum),
                                   y = TWgm3_avg, fill = daylight))+
    geom_errorbar(aes(ymin = TWgm3_avg - sd, ymax= TWgm3_avg + sd, colour = factor(daylight)),
                width = 0.3, position = position_dodge(0)) +
  #geom_errorbar(aes(ymin=y, ymax=y_upper.error), colour="blue", width = 0.1) +
  #geom_errorbar(aes(ymin=y_lower.error, ymax=y), colour="red", width = 0.1) +
  xlab("Depth Stratum")+
  ylab("Ctenophore: Standardised wet weight (g/m^3)")+
  #scale_x_discrete(limits = c(-0.9,0.9))+
  scale_colour_manual("daylight",values=c("light blue","dark blue"))+
  scale_fill_manual("daylight",values=c("light blue","dark blue"))+
  geom_col()+
  coord_flip()+
  facet_grid(~Site)+
  theme_bw()
plot(Ind_S_M20_ACAt_plot)
ggsave("figures/Paper/Ctenophore.jpg")

```


Siphonophore
```{r Siphonophore}

# Siphonophore
Ind_S_M20_ACAt <- S_M20_ACAt%>% 
  group_by(Site,daylight,Depth_Stratum,Deployment) %>% 
  filter(ACat=="Siphonophore") %>% 
  filter(Depth_Stratum == "Meso"|Depth_Stratum == "Epi"| Depth_Stratum =="Lmeso") %>% 
  #mutate(Weight_Std_gm3 = ifelse(daylight %in% "Night", Weight_Std_gm3*-1, weight_g)) %>% 
  summarise(TWgm3 = sum(Weight_gm3)) %>% 
  mutate(TWgm3 = ifelse(daylight %in% "Night", TWgm3*-1, TWgm3)) %>% 
  group_by(Site, daylight,Depth_Stratum) %>% 
  summarise(TWgm3_avg = mean(TWgm3),n(),sd=sd(TWgm3,na.rm = TRUE))
Ind_S_M20_ACAt$Site <- factor(as.factor(Ind_S_M20_ACAt$Site), levels = c("SOTS","55S","58S"))
Ind_S_M20_ACAt$Depth_Stratum <- factor(as.factor(Ind_S_M20_ACAt$Depth_Stratum),levels = c("Lmeso", "Meso", "Epi"))
Ind_S_M20_ACAt_plot <- ggplot(Ind_S_M20_ACAt,
                     mapping = aes(x = as.factor(Depth_Stratum),
                                   y = TWgm3_avg, fill = daylight))+
    geom_errorbar(aes(ymin = TWgm3_avg - sd, ymax= TWgm3_avg + sd, colour = factor(daylight)),
                width = 0.3, position = position_dodge(0)) +
  #geom_errorbar(aes(ymin=y, ymax=y_upper.error), colour="blue", width = 0.1) +
  #geom_errorbar(aes(ymin=y_lower.error, ymax=y), colour="red", width = 0.1) +
  xlab("Depth Stratum")+
  ylab("Siphonophore: Standardised wet weight (g/m^3)")+
  #scale_x_discrete(limits = c(-0.9,0.9))+
  scale_colour_manual("daylight",values=c("light blue","dark blue"))+
  scale_fill_manual("daylight",values=c("light blue","dark blue"))+
  geom_col()+
  coord_flip()+
  facet_grid(~Site)+
  theme_bw()
plot(Ind_S_M20_ACAt_plot)
ggsave("figures/Paper/Siphonophore.jpg")
```

Medusa
```{r Medusa}

# Medusa
Ind_S_M20_ACAt <- S_M20_ACAt%>% 
  group_by(Site,daylight,Depth_Stratum,Deployment) %>% 
  filter(ACat=="Medusa") %>% 
  filter(Depth_Stratum == "Meso"|Depth_Stratum == "Epi"| Depth_Stratum =="Lmeso") %>% 
  #mutate(Weight_Std_gm3 = ifelse(daylight %in% "Night", Weight_Std_gm3*-1, weight_g)) %>% 
  summarise(TWgm3 = sum(Weight_gm3)) %>% 
  mutate(TWgm3 = ifelse(daylight %in% "Night", TWgm3*-1, TWgm3)) %>% 
  group_by(Site, daylight,Depth_Stratum) %>% 
  summarise(TWgm3_avg = mean(TWgm3),n(),sd=sd(TWgm3,na.rm = TRUE))
Ind_S_M20_ACAt$Site <- factor(as.factor(Ind_S_M20_ACAt$Site), levels = c("SOTS","55S","58S"))
Ind_S_M20_ACAt$Depth_Stratum <- factor(as.factor(Ind_S_M20_ACAt$Depth_Stratum),levels = c("Lmeso", "Meso", "Epi"))
Ind_S_M20_ACAt_plot <- ggplot(Ind_S_M20_ACAt,
                     mapping = aes(x = as.factor(Depth_Stratum),
                                   y = TWgm3_avg, fill = daylight))+
    geom_errorbar(aes(ymin = TWgm3_avg - sd, ymax= TWgm3_avg + sd, colour = factor(daylight)),
                width = 0.3, position = position_dodge(0)) +
  #geom_errorbar(aes(ymin=y, ymax=y_upper.error), colour="blue", width = 0.1) +
  #geom_errorbar(aes(ymin=y_lower.error, ymax=y), colour="red", width = 0.1) +
  xlab("Depth Stratum")+
  ylab("Medusa: Standardised wet weight (g/m^3)")+
  #scale_x_discrete(limits = c(-0.9,0.9))+
  scale_colour_manual("daylight",values=c("light blue","dark blue"))+
  scale_fill_manual("daylight",values=c("light blue","dark blue"))+
  geom_col()+
  coord_flip()+
  facet_grid(~Site)+
  theme_bw()
plot(Ind_S_M20_ACAt_plot)
ggsave("figures/Paper/Medusa.jpg")

```

Salps
```{r Salps}

# Tunicates
Ind_S_M20_ACAt <- S_M20_ACAt%>% 
  group_by(Site,daylight,Depth_Stratum,Deployment) %>% 
  filter(ACat=="Salp") %>% 
  filter(Depth_Stratum == "Meso"|Depth_Stratum == "Epi"| Depth_Stratum =="Lmeso") %>% 
  #mutate(Weight_Std_gm3 = ifelse(daylight %in% "Night", Weight_Std_gm3*-1, weight_g)) %>% 
  summarise(TWgm3 = sum(Weight_gm3)) %>% 
  mutate(TWgm3 = ifelse(daylight %in% "Night", TWgm3*-1, TWgm3)) %>% 
  group_by(Site, daylight,Depth_Stratum) %>% 
  summarise(TWgm3_avg = mean(TWgm3),n(),sd=sd(TWgm3,na.rm = TRUE))
Ind_S_M20_ACAt$Site <- factor(as.factor(Ind_S_M20_ACAt$Site), levels = c("SOTS","55S","58S"))
Ind_S_M20_ACAt$Depth_Stratum <- factor(as.factor(Ind_S_M20_ACAt$Depth_Stratum),levels = c("Lmeso", "Meso", "Epi"))
Ind_S_M20_ACAt_plot <- ggplot(Ind_S_M20_ACAt,
                     mapping = aes(x = as.factor(Depth_Stratum),
                                   y = TWgm3_avg, fill = daylight))+
    geom_errorbar(aes(ymin = TWgm3_avg - sd, ymax= TWgm3_avg + sd, colour = factor(daylight)),
                width = 0.3, position = position_dodge(0)) +
  #geom_errorbar(aes(ymin=y, ymax=y_upper.error), colour="blue", width = 0.1) +
  #geom_errorbar(aes(ymin=y_lower.error, ymax=y), colour="red", width = 0.1) +
  xlab("Depth Stratum")+
  ylab("Salps: Standardised wet weight (g/m^3)")+
  #scale_x_discrete(limits = c(-0.9,0.9))+
  scale_colour_manual("daylight",values=c("light blue","dark blue"))+
  scale_fill_manual("daylight",values=c("light blue","dark blue"))+
  geom_col()+
  coord_flip()+
  facet_grid(~Site)+
  theme_bw()
plot(Ind_S_M20_ACAt_plot)
ggsave("figures/Paper/Salps.jpg")

```
pyrosome
```{r pyrosome}

# Tunicates
Ind_S_M20_ACAt <- S_M20_ACAt%>% 
  group_by(Site,daylight,Depth_Stratum,Deployment) %>% 
  filter(ACat=="Pyrosome") %>% 
  filter(Depth_Stratum == "Meso"|Depth_Stratum == "Epi"| Depth_Stratum =="Lmeso") %>% 
  #mutate(Weight_Std_gm3 = ifelse(daylight %in% "Night", Weight_Std_gm3*-1, weight_g)) %>% 
  summarise(TWgm3 = sum(Weight_gm3)) %>% 
  mutate(TWgm3 = ifelse(daylight %in% "Night", TWgm3*-1, TWgm3)) %>% 
  group_by(Site, daylight,Depth_Stratum) %>% 
  summarise(TWgm3_avg = mean(TWgm3),n(),sd=sd(TWgm3,na.rm = TRUE))
Ind_S_M20_ACAt$Site <- factor(as.factor(Ind_S_M20_ACAt$Site), levels = c("SOTS","55S","58S"))
Ind_S_M20_ACAt$Depth_Stratum <- factor(as.factor(Ind_S_M20_ACAt$Depth_Stratum),levels = c("Lmeso", "Meso", "Epi"))
Ind_S_M20_ACAt_plot <- ggplot(Ind_S_M20_ACAt,
                     mapping = aes(x = as.factor(Depth_Stratum),
                                   y = TWgm3_avg, fill = daylight))+
    geom_errorbar(aes(ymin = TWgm3_avg - sd, ymax= TWgm3_avg + sd, colour = factor(daylight)),
                width = 0.3, position = position_dodge(0)) +
  #geom_errorbar(aes(ymin=y, ymax=y_upper.error), colour="blue", width = 0.1) +
  #geom_errorbar(aes(ymin=y_lower.error, ymax=y), colour="red", width = 0.1) +
  xlab("Depth Stratum")+
  ylab("Pyrosome: Standardised wet weight (g/m^3)")+
  #scale_x_discrete(limits = c(-0.9,0.9))+
  scale_colour_manual("daylight",values=c("light blue","dark blue"))+
  scale_fill_manual("daylight",values=c("light blue","dark blue"))+
  geom_col()+
  coord_flip()+
  facet_grid(~Site)+
  theme_bw()
plot(Ind_S_M20_ACAt_plot)
ggsave("figures/Paper/Pyrosome.jpg")

```
#############################
# Gelatinous bladder: use data from ccomp_Acoustic_Category_M - G_nGB
G_GB <- S_M20_Acoustic_Category%>% 
  group_by(Site,daylight,Depth_Stratum,Deployment) %>% 
  filter(Acoustic_Category=="G_nGB") %>% 
 # filter(Taxa_updated =="Lampanyctus australis") %>% 
  filter(Depth_Stratum == "Meso"|Depth_Stratum == "Epi"| Depth_Stratum =="Lmeso") %>% 
  #mutate(Weight_Std_gm3 = ifelse(daylight %in% "Night", Weight_Std_gm3*-1, weight_g)) %>% 
  summarise(TWgm3 = sum(Weight_gm3)) %>% 
  mutate(TWgm3 = ifelse(daylight %in% "Night", TWgm3*-1, TWgm3)) %>% 
  group_by(Site, daylight,Depth_Stratum) %>% 
  summarise(TWgm3_avg = mean(TWgm3),n(),sd=sd(TWgm3,na.rm = TRUE))
TW_std_ID_Taxa$Site <- factor(as.factor(TW_std_ID_Taxa$Site), levels = c("SOTS","55S","58S"))
TW_std_ID_Taxa$Depth_Stratum <- factor(as.factor(TW_std_ID_Taxa$Depth_Stratum),levels = c("Lmeso", "Meso", "Epi"))
Taxa_Ind_plot <- ggplot(G_GB,
                     mapping = aes(x = as.factor(Depth_Stratum),
                                   y = TWgm3_avg, fill = daylight))+
    geom_errorbar(aes(ymin = TWgm3_avg - sd, ymax= TWgm3_avg + sd, colour = factor(daylight)),
                width = 0.3, position = position_dodge(0)) +
  #geom_errorbar(aes(ymin=y, ymax=y_upper.error), colour="blue", width = 0.1) +
  #geom_errorbar(aes(ymin=y_lower.error, ymax=y), colour="red", width = 0.1) +
  xlab("Depth Stratum")+
  ylab("G_nGB: Standardised wet weight (g/m^3)")+
  #scale_x_discrete(limits = c(-0.9,0.9))+
  scale_colour_manual("daylight",values=c("light blue","dark blue"))+
  scale_fill_manual("daylight",values=c("light blue","dark blue"))+
  geom_col()+
  coord_flip()+
  facet_grid(~Site)+
  theme_bw()
plot(G_GB)
ggsave("figures/G_nGB.jpg")

```


